% -*- mode: latex -*-

\mansection{fsqp}
\begin{mandesc}
  \short{fsqp}{sequentially related FSQP solver}\\ % @mandesc@
\end{mandesc}
%-- Calling sequence section
\begin{calling_sequence}
\begin{verbatim}
  x=srfsqp(x0,ipar,srpar,mesh_pts,rpar,[bl,bu],obj,cntr,grob,grcn)  
  x=srfsqp(x0,ipar,srpar,mesh_pts,rpar,[bl,bu],obj,cntr,'grob','grcn')  
  x=srfsqp(x0,ipar,srpar,mesh_pts,rpar,[bl,bu],'obj','cntr','grob','grcn', [cd])  
  x=srfsqp(x0,ipar,srpar,mesh_pts,rpar,[bl,bu],'obj','cntr','grobfd','grcnfd', [cd])  
  [x,inform]=srfsqp(...)  
  [x,inform,f,g,lambda]=srfsqp(...)  
\end{verbatim}
\end{calling_sequence}

%-- Parameters
\begin{parameters}
  \begin{varlist}
    \vname{x0}
    : real column vector (initial guess)
    \vname{ipar}
    : integer vector of size 8.
    \vname{srpar}
    : integer vector of size 3.
    \vname{mesh\_pts}
    : integer vector of size nfsr+ncsrn+ncsrl
    \vname{rpar}
    : real vector of size 4.
    \vname{[bl,bu]}
    : real matrix with 2 columns and same row dimension as x.
    \vname{obj, cntr}
    : name of scilab functions or character strings (name of C functions) defining the objective function and the constraints function.
    \vname{grob,grcn}
    : name of scilab functions or character strings (name of C functions) defining the gradient of objective function and the gradient of  constraints function.
    \vname{cd}
    : optional real vector (argument passed to C functions).
  \end{varlist}
\end{parameters}

\begin{mandescription}
  
  fsqp interface for SR problems. This interface uses the notations of the cfsqp
  user's guide (see c\_manual.ps).
  The four functions (objective, constraints, gradient-of-objective,
  gradient-of-constraints) can be given either as C-functions dynamically
  linked with Scilab or as Scilab functions (mixtures are allowed).
  If a Scilab function is given as argument of fsqp, 
  just use its name (without quotes). If a C function is to be called,
  use a character string to define it. For instance fsqp(...,obj,...)
  invokes fsqp with the Scilab function \verb!obj! and
  \verb!fsqp(...,"obj",...)! invokes fsqp with the C function 
  \verb!obj!, linked with Scilab by e.g. \verb! link("obj.o", "obj") !.
  
  The chains "grobfd" and "grcnfd" can be used as C functions to compute
  the gradients of the functions grob and cntr by finite difference.
  Notations:
  
  \begin{mintednsp}{nsp}
    ipar=[nf,nineqn,nineq,neqn,neq,modefsqp,miter,iprint];
    srpar=[nfsr,ncsrl,ncsrn];
    rpar=[bigbnd,eps,epsneq,udelta];
  \end{mintednsp}

  \begin{mintednsp}{nsp}
    function fj=obj(j,x)
    function  gj=cntr(j,x)
    function gradf=grob(j,x)
    function gradgj=grcn(j,x)
  \end{mintednsp}

  obj(j,x) returns the value of the jth objective, given x.
  cntr(j,x) returns the value of the jth constraint, given x.
  grob(j,x) (resp. grcn(j,x)) is the value at x of the gradient of the 
  function x-$>$obj(j,x) (resp.  x-$>$cntr(j,x)).
  
  It may be useful to make use of the fsqp C variable x\_is\_new and to
  evaluate these functions in a vector way. For instance the function
  cntr can be replaced by the following cntr2 function:
  
  \begin{mintednsp}{nsp}
    function cj=cntr2(j,x)
    if x_is_new() then
    all_objectives=allobj(x);
    all_constraints=allcntr(x);
    all_gradobjectives=allgrob(x);
    all_gradconstraints=allgrcn(x);
    cj=all_constraints(j);
    set_x_is_new(0);  //Use resume to define global Scilab variables
    [all_objectives,all_constraints,all_gradobjectives,all_gradconstraints]=....
    resume(all_objectives,all_constraints,all_gradobjectives,all_gradconstraints);
    else
    cj=all_constraints(j);
    end
  \end{mintednsp}

  Here, the function allcntr(x) returns a vector all\_constraints whose
  jth component all\_constraints(j) is cntr(j).
  A typical example comes from discretized semi-infinite program. 
  See example5.sci.
  
\end{mandescription}

%--example
\begin{examples}
  \begin{mintednsp}{nsp}
    //See the script file example2.sce
  \end{mintednsp}
\end{examples}

%-- see also
\begin{manseealso}
  \manlink{fsqp}{fsqp} \manlink{x\_is\_new}{x-is-new} \manlink{set\_x\_is\_new}{set-x-is-new} 
\end{manseealso}

