% -*- mode: latex -*-

\mansection{quapro}
\begin{mandesc}
  \short{quapro}{linear quadratic programming solver (external toolbox)}
\end{mandesc}
\index{quapro}\label{quapro}
\begin{calling_sequence}
  \begin{verbatim}
    [x,lagr,f]=quapro(Q,p,C,b,ci,cs,me,x0=val,mode=int,imp=int)  
  \end{verbatim}
\end{calling_sequence}
%-- Parameters
\begin{parameters}
  \begin{varlist}
    \vname{Q}: real symmetric matrix (dimension \verb!n x n!).
    \vname{p}: real (column) vector (dimension \verb! n!)
    \vname{C}: real matrix (dimension \verb! (me + md) x n!) (If no constraints are given, you can set \verb!C = []!)
    \vname{b}: RHS column vector (dimension \verb! (me + md)!) (If no constraints are given, you can set \verb!b = []!)
    \vname{ci}: column vector of lower-bounds (dimension \verb!n!). If there are no lower bound constraints, put \verb!ci = []!. 
    If some components of \verb!x! are bounded from below, set the other (unconstrained) values of \verb!ci! to a very  
    large negative number (e.g. \verb!ci(j) = -number_properties('huge')!.
   \vname{cs}: column vector of upper-bounds. (Same remarks as above).
   \vname{me}: number of equality constraints (i.e. \verb!C(1:me,:)*x = b(1:me)!)
   \vname{mode}: If \verb!mode=1'! the calculated initial feasible point is a vertex. If \verb!mode=2! the calculated initial feasible point is arbitrary.
   \vname{x0}: In that case an initial point is given and \verb!mode'! is ignored and set to \verb!mode=3!. The given point must be admissible.
   \vname{imp}: verbose option (optional parameter)   (Try \verb!imp=7,8,...!). warning the message are output in the window where scilab has been started.
   \vname{x}: optimal solution found.
   \vname{f}: optimal value of the cost function (i.e. \verb!f=0.5*x'*Q*x+p'*x!).
   \vname{lagr}: vector of Lagrange multipliers.  If lower and upper-bounds \verb!ci,cs! are provided, \verb!lagr! has 
   \verb!n + me + md! components and \verb!lagr(1:n)! is the Lagrange  vector associated with the bound 
   constraints and  \verb!lagr (n+1 : n + me + md)! is the Lagrange vector associated  
   with the linear constraints. (If an upper-bound (resp. lower-bound) constraint \verb!i! is active 
   \verb!lagr(i)! is $>$ 0 (resp. $<$0). If no bounds are provided, \verb!lagr! has only \verb!me + md! components.
  \end{varlist}
\end{parameters}

\begin{mandescription}

Note that \verb!quapro! is not directly accessible in nsp. You need 
to download a toolbox and ask the authors for using it. 

\begin{itemize}
\item \verb![x,lagr,f]=quapro(Q,p,C,b,[],[],0)!
\begin{equation*}
\begin{split}
  \min_{x}& \hspace{1cm}  \frac{1}{2} x^T Q x + p^T *x \\
  C x \le b  & \\
\end{split}
\end{equation*}
\item  \verb![x,lagr,f]=quapro(Q,p,C,b,ci,cs,0)!
\begin{equation*}
\begin{split}
  \min_{x} &\hspace{1cm}  \frac{1}{2} x^T Q x + p^T *x \\
  C x \le b  & \\
  ci \le x \le cs & \\
\end{split}
\end{equation*}
\item \verb![x,lagr,f]=quapro(Q,p,C,b,ci,cs,me)!
\begin{equation*}
\begin{split}
  \min_{x} &\hspace{1cm}  \frac{1}{2} x^T Q x + p^T *x \\
  C(j,:) x = b(j) , \,  j \in [1,me] & \\
  C(j,:) x \le b(j), \, j \in [me+1,md] & \\
  ci \le x \le cs &\\
\end{split}
\end{equation*}
\end{itemize}
  If no initial point is given the
  program computes a feasible initial point
  which is a vertex of the region of feasible points if
  \verb!x0='v'!.
  If \verb!x0='g'!, the program computes a feasible initial 
  point which is not necessarily a vertex. This mode is
  advisable when the quadratic form is positive
  definite and there are  few constraints in
  the problem or when there are large bounds
  on the variables that are just security bounds and
  very likely not active at the optimal solution.
  Note that \verb!Q! is not necessarily non-negative, i.e.
  \verb!Q! may have negative eigenvalues.
\end{mandescription}
\begin{examples}
  \begin{mintednsp}{nspxxx}
    //Find x in R^6 such that:
    //C1*x = b1 (3 equality constraints i.e me=3)
    C1= [1,-1,1,0,3,1;
        -1,0,-3,-4,5,6;
        2,5,3,0,1,0];
    b1=[1;2;3];
    //C2*x $<$= b2 (2 inequality constraints)
    C2=[0,1,0,1,2,-1;  -1,0,2,1,1,0];
    b2=[-1;2.5];
    //with  x between ci and cs:
    ci=[-1000;-10000;0;-1000;-1000;-1000];cs=[10000;100;1.5;100;100;1000];
    //and minimize 0.5*x'*Q*x + p'*x with
    p=[1;2;3;4;5;6]; Q=eye(6,6);
    //No initial point is given;
    C=[C1;C2] ; //
    b=[b1;b2] ;  //
    me=3;
    if exists('quapro','function') then 
     [x,lagr,f]=quapro(Q,p,C,b,ci,cs,me)
     //Only linear constraints (1 to 4) are active (lagr(1:6)=0):
     [x,lagr,f]=quapro(Q,p,C,b,[],[],me)   //Same result as above 
    end
\end{mintednsp} 
\end{examples}
%-- see also
\begin{manseealso}
%%  \manlink{linpro}{linpro} \manlink{optim}{optim}  
\end{manseealso}

\begin{authors}
  \paragraph{Eduardo Casas  Renteria} , Universidad de Cantabria,
  \paragraph{Cecilia Pola Mendez}  , Universidad de Cantabria 
\end{authors}
