% -*- mode: latex -*-
\mansection{all}
\begin{mandesc}
  \short{all}{checks if all elements are nonzero or true} 
\end{mandesc}

\begin{calling_sequence}
\begin{verbatim}
 B= all(A [,dim=val])
 B= all(A [,val])
\end{verbatim}
\end{calling_sequence}
% -- Parameters
\begin{parameters}
  \begin{varlist}
    \vname{A}:  matrix of numbers or booleans 
    \vname{B}: a boolean matrix 
    \vname{val}: optional argument chosen among the possible strings '*', 
    'full', 'FULL', 'row', 'ROW', 'col', or 'COL'  or an non ambiguous abbreviation or an 
    integer as follows $0$ for 'full', $1$ for 'row', $2$ for 'column'.
  \end{varlist}
\end{parameters}

\begin{mandescription}
  \verb!all! checks if elements are nonzero (resp. are true) when a matrix of numbers (resp. of booleans) 
  is given as argument. The size of the result and the number of arguments taken in consideration depends 
  on the optional argument \verb!dim! as follows:
  \begin{itemize}
  \item \verb!'*'! The answer is scalar and true if all the elements are nonzero (resp. are true).
  \item \verb!'r'! The answer is a row vector which contains true value when all the elements of 
    the corresponding column of the matrix are  nonzero (resp. are true). 
  \item \verb!'c'! The answer is a column vector which contains true value when all the elements of 
    the corresponding row of the matrix are  nonzero (resp. are true).
  \end{itemize}
  The default behaviour is to follow the Matlab rules i.e the mode is by default \verb!'r'! 
  for a matrix except for row vectors for which the defaultmode is \verb!'*'!. 
  This mode should also be obtained by \verb!'m'! in a near future. 
\end{mandescription}
%-- see also
\begin{manseealso}
  \manlink{any}{any}, \manlink{and}{and}, \manlink{or}{or}, \manlink{not}{not}
\end{manseealso}
%-- Authors


