% -*- mode: latex -*-
\mansection{and, or}
\begin{mandesc}
  \short{and}{logical AND function or operator}\\
  \short{or}{logical OR function or operator}
\end{mandesc}

%-- Calling sequence section
\begin{calling_sequence}
\begin{verbatim}
  C = and(A)
  C = and(A,dim=dimarg)
  C = A & B  // or  C = and(A,B)
  C = A && B 
  C = or(A)
  C = or(A,dim=dimarg)
  C = A | B  // or C = or(A,B)
  C = A || B 
\end{verbatim}
\end{calling_sequence}
% -- Parameters
\begin{parameters}
  \begin{varlist}
    \vname{A,B,C}: boolean matrices. 
    \vname{dimarg}: a string (\verb!'*'!,or \verb!'r'!,or \verb!'c'!) or an integer which defines 
    a dimension along which the boolean AND or OR operation is performed. 
  \end{varlist}
\end{parameters}

\begin{mandescription}
  \begin{itemize} 
  \item \itemdesc{and}
  \begin{itemize} 
  \item \verb!and(A)! is the logical AND of the elements of the boolean matrix \verb!A!. 
    \verb!and(A)! returns \verb!%t! iff all entries of \verb!A! are \verb!%t!. 
  \item \verb!and(A,dim='r')! or \verb!and(A,dim=1)!
    returns a boolean row vector such that its j th component is the logical AND of the 
    elements $A(i,j),i=1,m$
  \item \verb!and(A,dim='c')! or \verb!and(A,dim=2)! returns a boolean colum vector 
    such that its i th component is the logical AND of the elements $A(i,j),j=1,n$.
  \item \verb!A & B! or \verb!and(A,B)! gives the element-wise logical AND
    of the booleans matrices \verb!A! and  \verb!B!. The two matrices must have the same size 
    with the usual promotion of single booleans (\verb!1x1! matrices). 
  \item \verb!A && B! performs a sequential AND ; this is the same than 
    the element-wise logical AND but when $A(i,j)$ is false, the result $C(i,j)$
    is directly set to false, $B(i,j)$ being not evaluated.
  \end{itemize}
  \item \itemdesc{or}
  \begin{itemize} 
  \item \verb!or(A)! is the logical OR of the elements of the boolean matrix \verb!A!. 
    \verb!or(A)! returns \verb!%t! iff at least one entry of \verb!A! is \verb!%t!. 
  \item \verb!or(A,dim='r')! or \verb!or(A,dim=1)!
    returns a boolean row vector such that its j th component is the logical OR of the 
    elements $A(i,j),i=1,m$
  \item \verb!or(A,dim='c')! or \verb!or(A,dim=2)! returns a boolean colum vector 
    such that its i th component is the logical OR of the elements $A(i,j),j=1,n$.
  \item \verb!A | B! or \verb!or(A,B)! gives the element-wise logical  OR
    of the booleans matrices \verb!A! and  \verb!B!. The two matrices must have the same size 
    with the usual promotion of single booleans (\verb!1x1! matrices). 
  \item \verb!A || B! performs a sequential OR ; this is the same than 
    the element-wise logical OR but when $A(i,j)$ is true, the result $C(i,j)$
    is directly set to true, $B(i,j)$ being not evaluated.
  \end{itemize} 
\end{itemize}

\end{mandescription}

%--example 
\begin{examples}
\paragraph{AND basic examples}
\begin{Verbatim}
A = [%t, %f, %t; %t, %t, %f; %t, %t, %t]
and(A)
and(A,dim=1)
and(A,dim=2)
B = rand(3,3) < 0.5
A & B
A && B

// difference between & and &&
i = 0;
x = rand(1,3)
bool = i > 0  &&  x(i) < 0.5 // the 2d expression is not evaluated
bool = i > 0  &   x(i) < 0.5 // the 2d expression is evaluated and so raise an error
\end{Verbatim}

\paragraph{OR basic examples}
\begin{Verbatim}
A = [%t, %f, %f; %t, %t, %f; %f, %f, %f]
or(A)
or(A,dim=1)
or(A,dim=2)
B = rand(3,3) < 0.5
A | B
A || B
    
// difference between | and || 
i = 0;
x = rand(1,3)
bool = i == 0 || x(i) < 0.5 // the 2d expression is not evaluated
bool = i == 0 || x(i) < 0.5 // the 2d expression is evaluated and so raise an error
\end{Verbatim}

\end{examples}

%-- see also
\begin{manseealso}
  \manlink{not}{not},\manlink{any}{any}, \manlink{all}{all}  

\end{manseealso}

