% -*- mode: latex -*-
\mansection{any}
\begin{mandesc}
  \short{any}{checks if any element is nonzero or true} 
\end{mandesc}
\begin{calling_sequence}
\begin{verbatim}
 B= any(A [,dim=val])
 B= any(A [,val])
\end{verbatim}
\end{calling_sequence}
% -- Parameters
\begin{parameters}
  \begin{varlist}
    \vname{A}:  matrix of numbers or booleans 
    \vname{B}: a boolean matrix 
    \vname{dim=val} optional argument chosen among the possible strings '*', 
    'full', 'FULL', 'row', 'ROW', 'col', or 'COL'  or an non ambiguous abbreviation or an 
    integer as follows $0$ for 'full', $1$ for 'row', $2$ for 'column'.
  \end{varlist}
\end{parameters}

\begin{mandescription}
  \verb!any! checks if any elements are nonzero (resp. are true) when a matrix of numbers (resp. of booleans) 
  is given as argument. The size of the result and the elements of the matrix taken in consideration depends 
  on the optional argument \verb!dim! as follows~:
  \begin{itemize}
  \item \verb!'*'! The answer is scalar and equal to true if any element of the matrix \verb!A!
    are nonzero (resp. are true).
  \item \verb!'r'! The answer is a row vector which contains true value when any element of 
    the corresponding column of the matrix is nonzero (resp. is true). 
  \item \verb!'c'! The answer is a column vector which contains true value when any element of 
    the corresponding row of the matrix is nonzero (resp. is true).
  \end{itemize}
  The default behaviour is to follow the Matlab rules i.e the mode is by default \verb!'r'! 
  for a matrix except for row vectors for which the defaultmode is \verb!'*'!. 
  This mode should also be obtained by \verb!'m'! in a near future. 
\end{mandescription}
%-- see also
\begin{manseealso}
  \manlink{all}{all}, \manlink{and}{and}, \manlink{or}{or}, \manlink{not}{not}
\end{manseealso}
%-- Authors

