% -*- mode: latex -*-
%% Scilab ( http://www.scilab.org/ ) - This file is part of Scilab
%% Copyright (C) 1987-2016 - F. Delebecque
%%
%% This program is free software; you can redistribute it and/or modify
%% it under the terms of the GNU General Public License as published by
%% the Free Software Foundation; either version 2 of the License, or
%% (at your option) any later version.
%%
%% This program is distributed in the hope that it will be useful,
%% but WITHOUT ANY WARRANTY; without even the implied warranty of
%% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
%% GNU General Public License for more details.
%%
%% You should have received a copy of the GNU General Public License
%% along with this program; if not, write to the Free Software
%% Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307  USA
%%                                                                                                

\mansection{aff2ab}
\begin{mandesc}
  \short{aff2ab}{linear (affine) function to A,b conversion} \\ % 
\end{mandesc}
%\index{aff2ab}\label{aff2ab}
%-- Calling sequence section
\begin{calling_sequence}
\begin{verbatim}
  [A,b]=aff2ab(afunction,dimX,D [,flag])  
\end{verbatim}
\end{calling_sequence}
%-- Parameters
\begin{parameters}
  \begin{varlist}
    \vname{afunction}: a scilab function \verb! Y =fct(X,D) ! 
    where \verb!X, D, Y! are \verb!list! of matrices
    \vname{dimX}: a \verb!p! x \verb!2! integer matrix 
    (\verb!p! is the number of matrices in \verb!X!)
    \vname{D}: a \verb!list! of real matrices (or any other valid Scilab object).
    \vname{flag}: optional parameter (\verb!flag='f'! or \verb!flag='sp'!)
    \vname{A}: a real matrix
    \vname{b}: a real vector having same row dimension as \verb!A!
  \end{varlist}
\end{parameters}
\begin{mandescription}
  \verb!aff2ab! returns the matrix representation of an affine
  function (in the canonical basis). The given function \verb!afunction!
  should have the following prototype:
  \verb! Y=afunction(X,D)!  where \verb! X=list(X1,X2,...,Xp)! is
  a list of p real matrices, and \verb! Y=list(Y1,...,Yq)! is
  a list of q real real matrices which depend linearly of
  the \verb!Xi!'s. The (optional) input argument \verb!D! contains 
  parameters needed to compute Y as a function of X and it is generally 
  a list of matrices. The parameter \verb!dimX! is a \verb!p! x \verb!2! matrix: 
  \verb!dimX(i)=[nri,nci]! is the actual number of rows and columns of matrix \verb!Xi!.
  These dimensions determine \verb!na!, the column dimension of 
  the resulting matrix \verb!A!: \verb!na=nr1*nc1 +...+ nrp*ncp!.
  If the optional parameter \verb!flag='sp'! the resulting \verb!A!
  matrix is returned as a sparse matrix.
  This function is useful to solve a system of linear equations
  where the unknown variables are matrices.
\end{mandescription}
%--example 
\begin{examples}
  Lyapunov equation solver (one unknown variable, one constraint)
  \begin{mintednsp}{nsp}
    function Y=lyapunov(X,D)
      [A,Q]=D(:);Xm=X(:); Y=list(A'*Xm+Xm*A-Q);
    endfunction;
    A=rand(3,3);Q=rand(3,3);Q=Q+Q';D=list(A,Q);dimX=[3,3];
    [Aly,bly]=aff2ab(lyapunov,dimX,D);
    [Xl,kerA]=linsolve(Aly,bly); Xv=vec2list(Xl,dimX); 
    lyapunov(Xv,D)
    Xm=Xv(:); 
    if norm(A'*Xm+Xm*A-Q)> 1.e-10 then;pause;end
  \end{mintednsp}
    Lyapunov equation solver with redundant constraint X=X'
    (one variable, two constraints) D is global variable.
  \begin{mintednsp}{nsp}
    function Y=ly2(X,D)
      [A,Q]=D(:);Xm=X(:); Y=list(A'*Xm+Xm*A-Q,Xm'-Xm);
    endfunction;
    A=rand(3,3);Q=rand(3,3);Q=Q+Q';D=list(A,Q);dimX=[3,3];
    [Aly,bly]=aff2ab(ly2,dimX,D);
    [Xl,kerA]=linsolve(Aly,bly); Xv=vec2list(Xl,dimX);
    res = ly2(Xv,D); 
    if norm(res(1)) > 1.e-10 then;pause;end
    if norm(res(2)) > 1.e-10 then;pause;end
  \end{mintednsp}
  Francis equations, find matrices \verb!X1! and \verb!X2! such that:
    \begin{align*}
      A1*X1 & - X1*A2 + B*X2 -A3 = 0\\
      D1*X1 & -D2 = 0 
    \end{align*}
  \begin{mintednsp}{nsp}
    function Y=bruce(X,D)
      [A1,A2,A3,B,D1,D2]=D(:),...
      [X1,X2]=X(:);Y=list(A1*X1-X1*A2+B*X2-A3,D1*X1-D2);
    endfunction
    A1=[-4,10;-1,2];A3=[1;2];B=[0;1];A2=1;D1=[0,1];D2=1;
    D=list(A1,A2,A3,B,D1,D2);
    [n1,m1]=size(A1);[n2,m2]=size(A2);[n3,m3]=size(B);
    dimX=[[m1,n2];[m3,m2]];
    [Af,bf]=aff2ab(bruce,dimX,D);
    [Xf,KerAf]=linsolve(Af,bf);Xsol=vec2list(Xf,dimX)
    res = bruce(Xsol,D);
    if norm(res(1)) > 1.e-10 then;pause;end
    if norm(res(2)) > 1.e-10 then;pause;end
  \end{mintednsp}
  Find all X which commute with A
  \begin{mintednsp}{nsp}
    function y=f(X,D) 
      y=list(D(:)*X(:)-X(:)*D(:));
    endfunction;
    A=rand(3,3);dimX=[3,3];[Af,bf]=aff2ab(f,dimX,list(A));
    [Xf,KerAf]=linsolve(Af,bf);[p,q]=size(KerAf);
    Xsol=vec2list(Xf+KerAf*rand(q,1),dimX);
    C=Xsol(:); 
    if norm(A*C-C*A) > 1.e-10 then pause;end
  \end{mintednsp}
\end{examples}
%-- see also
\begin{manseealso}
  \manlink{linsolve}{linsolve}  
\end{manseealso}

\begin{authors}
  François Delebecque
\end{authors}
