% -*- mode: latex -*-
%% Nsp
%% Copyright (C) 1998-2015 Jean-Philippe Chancelier Enpc/Cermics, Bruno Pinçon Esial/Iecn
%%
%% This library is free software; you can redistribute it and/or
%% modify it under the terms of the GNU General Public
%% License as published by the Free Software Foundation; either
%% version 2 of the License, or (at your option) any later version.
%%
%% This library is distributed in the hope that it will be useful,
%% but WITHOUT ANY WARRANTY; without even the implied warranty of
%% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the GNU
%% General Public License for more details.
%%
%% You should have received a copy of the GNU General Public
%% License along with this library; if not, write to the
%% Free Software Foundation, Inc., 59 Temple Place - Suite 330,
%% Boston, MA 02111-1307, USA.
%%
\mansection{norm}
\begin{mandesc}
  \short{norm}{vector and matrix norm}
\end{mandesc}
% -- Calling sequence section
\begin{calling_sequence}
\begin{verbatim}
nx = norm(x)
nx = norm(x,type_norm)
nA = norm(A)
nA = norm(A,type_norm)
\end{verbatim}
\end{calling_sequence}
% -- Parameters
\begin{parameters}
  \begin{varlist}
    \vname{x}:  numerical vector.
    \vname{A}:  numerical matrix.
    \vname{type_norm}: optional scalar or string chosen among
    \verb+1+, \verb+2+, \verb+%inf+ (in fact any real $p \ge 1$ for vectors),
    \verb+'1'+, \verb+'2'+, \verb+'inf'+. The default value is 2.
    \vname{nx,nA}: real positive scalar.
  \end{varlist}
\end{parameters}

\begin{mandescription}
This function computes vector or matrix norm according to the size, $m
\times n$, of the given first argument. When $m$ or $n$ is equal to 1 a vector
norm is computed and returned otherwise a matrix norm is computed and returned. 
The second argument could be a scalar and any real $p \ge 1$ could be used in case of a vector
$x$ to compute its $p-norm$ :
$x$ to compute its $p-norm$ :
$$
    ||x||_p = \left( \sum_{i=1}^n |x_i|^p \right)^{1/p}
$$
with the limit case of the inf-norm got using \verb+p=%inf+ :
$$
    ||x||_{\infty} = \max_i |x_i|
$$
For matrices, the \verb+1+, \verb+2+ and \verb+%inf+ ``induced matrix'' norms 
and the Frobenius norm are defined as follows:
$$
    ||A||_1 = \max_{||x||_1 = 1} ||Ax||_1 = \max_j \sum_i |A_{i,j}|  
$$
$$
    ||A||_2 = \max_{||x||_2 = 1} ||Ax||_2 = \sqrt{\max \mathop{\mathrm{spec}}(A^* A)}
$$
$$
    ||A||_{\infty} = \max_{||x||{\infty} = 1} ||Ax||_{\infty} = \max_i \sum_j |A_{i,j}|  
$$
$$
   ||A||_F =  \left( \sum_{i,j} A_{i,j}^2 \right)^{1/2}
$$
The Frobenius norm is computed by using  \verb+type_norm='fro' or 'Fro'+. 
Finally note that with \verb+type_norm='m' or 'M'+ the max 
of $|A_{i,j}|$ is computed but it is not a matrix norm.
\itemdesc{remark}
The matrix 2-norm is not available for sparse matrix.
\end{mandescription}
\begin{examples}
\paragraph{example 1} a simple example
\begin{mintednsp}{nsp}
x=[1,1];
// 1-norm
norm(x,1)  // or norm(x,'1')
// 2-norm
norm(x,2)  // or norm(x,'2') or simply norm(x)
// Inf-norm
norm(x,%inf)  // or norm(x,'Inf')
\end{mintednsp}

\paragraph{example 2} invariance of a 2-norm by an orthonormal tranformation
\begin{mintednsp}{nsp}
// make an orthonormal matrix
Q=qr(rand(5,5));
// a random vector
x = randn(5,1);
// its 2-norm
nx = norm(x,2)
// the 2-norm Q*x
ny = norm(Q*x, 2)
// nx and ny should be near equal
abs((nx-ny)/nx)
\end{mintednsp}
\end{examples}

%\begin{manseealso}
%  \manlink{qr}{qr}  
%\end{manseealso}

% -- Authors
\begin{authors}
   interface and some codes by Bruno Pincon and Jean-Philippe
   Chancelier. lapack routines dlange and zlange are used for
   1 and Inf matrix norms and dgesdd zgesdd for matrix 2-norm.
\end{authors}
