% -*- mode: latex -*-
%% Nsp
%% Copyright (C) 1998-2015 Jean-Philippe Chancelier Enpc/Cermics, Bruno Pinçon Esial/Iecn
%%
%% This library is free software; you can redistribute it and/or
%% modify it under the terms of the GNU General Public
%% License as published by the Free Software Foundation; either
%% version 2 of the License, or (at your option) any later version.
%%
%% This library is distributed in the hope that it will be useful,
%% but WITHOUT ANY WARRANTY; without even the implied warranty of
%% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the GNU
%% General Public License for more details.
%%
%% You should have received a copy of the GNU General Public
%% License along with this library; if not, write to the
%% Free Software Foundation, Inc., 59 Temple Place - Suite 330,
%% Boston, MA 02111-1307, USA.
%%
 

\mansection{solve}
\begin{mandesc}
  \short{solve}{solve a linear system}
\end{mandesc}
% -- Calling sequence section
\begin{calling_sequence}
\begin{verbatim}
 X= solve (A,b, mode=str)
\end{verbatim}
\end{calling_sequence}
% -- Parameters
\begin{parameters}
  \begin{varlist}
    \vname{A, b}: numerical matrices.
    \vname{mode}: a string.
  \end{varlist}
\end{parameters}

\begin{mandescription}
This function solves the linear system $Ax = b$. The resolution is 
controled by the optional mode parameter~:
\begin{itemize}
  \item \verb+"std"+: A is assumed square, LU decomposition is used 
    through lapack routines \verb+dgetrf+ and \verb+dgetrs+ 
    (\verb+zgetrf+ and \verb+zgetrs+ in the complex case).
  \item \verb+"sympos"+: A is symmetric positive definite and lapack routines 
    \verb+dpotrf+ and \verb+dpotrs+ (\verb+zpotrf+ and \verb+zpotrs+ for hermitian positive definite) are used. 
  \item \verb+"lo"+: A is assumed lower triangular (i.e only \verb+tril(A)+ is used) and the 
    system is solved using lapack routines \verb+dtrtrs+ (resp. \verb+ztrtrs+).
  \item \verb+"loT"+: like for \verb+"lo"+, A is assumed lower triangular but solve $A^T x=b$.
  \item \verb+"loH"+: like for \verb+"lo"+, A is assumed lower triangular but solve $A^H x=b$.
  \item \verb+"up"+: A is assumed upper triangular (i.e only \verb+triu(A)+ is used) and the system is 
    solved using lapack routines \verb+dtrtrs+ (resp. \verb+ztrtrs+).
  \item \verb+"upT"+: like for \verb+"up"+, A is assumed upper triangular but solve $A^T x=b$.
  \item \verb+"upH"+: like for \verb+"up"+, A is assumed upper triangular but solve $A^H x=b$.
  \item \verb+"lsq"+: The system is solved in the least-square sense using 
    lapack routines using lapack routines \verb+dgelsy+ (resp. \verb+zgelsy+).
  \item \verb+"\\"+ A previous routine is selected by checking properties of \verb+A+.
  \item \verb+"sym"+ A is symmetric and lapack routines 
    \verb+dsytrf+ and \verb+dsytrs+ (\verb+zsytrf+ and \verb+zsytrs+ for symmetric complex) are used. 
\end{itemize}
\end{mandescription}

\begin{examples}
  \paragraph{example 1} simple examples
  \begin{mintednsp}{nsp}
    n=10;b=rand(n,2);A=rand(n,n);
    x=solve(A,b,mode="std"); 
    if norm(A*x-b) > 1.e-10 then pause;end 
    // lower triangular
    x=solve(A,b,mode="lo"); 
    if norm(tril(A)*x-b)> 1.e-10  then pause;end 
    // upper triangular 
    x=solve(A,b,mode="up"); 
    if norm(triu(A)*x-b)> 1.e-10  then pause;end 
    // symetric 
    x=solve(A*A',b,mode="sym"); 
    if norm(A*A'*x-b)> 1.e-10 then pause;end 
    // least square 
    x=solve(A,b,mode="lsq"); 
    if norm(A*x-b)> 1.e-10 then pause;end 
    // symmetric positive definite 
    x=solve(A*A',b,mode="sympos"); 
    if norm(A*A'*x-b) > 1.e-7 then pause;end 
    b=rand(n,2);A=rand(n,n);
    A= A + %i*rand(n,n);
    // symetric 
    x=solve(A*A.',b,mode="sym"); 
    if norm(A*A.'*x-b)> 1.e-7 then pause;end 
    // hermitian positive definite 
    x=solve(A*A',b,mode="sympos"); 
    if norm(A*A'*x-b) > 1.e-7 then pause;end
  \end{mintednsp}

  \paragraph{example 2} Using solve with factorisations. When you factorize a square 
  matrix with \manlink{lu}{lu} or \manlink{chol}{chol} (or \manlink{qr}{qr}) you can
  use the backslash operator \verb+\+ to solve the triangular systems with efficiency
  (backslash detects the triangular matrix structure and call the good routine) but 
  using directly \verb+solve+ (with the good option) is faster.
  \begin{mintednsp}{nsp}
    n=800;b=rand(n,2);A=randn(n,n);
    [L,U,p] = lu(A); 
    // solving the 2 triangular system with backslash
    tic(); x = U\(L\b(p,:)); toc()
    norm(A*x-b,1)/norm(b) 
    // solving the 2 triangular system with solve
    tic(); x = solve(U, solve(L,b(p,:),mode="lo"), mode="up"); toc()
    norm(A*x-b,1)/norm(b) 
    // form a symetric positive definite matrix
    A = A'*A; // you can use pmult(A,A)
    C = chol(A); // C'C=A with C upper triangular  
    // solving the 2 triangular system with backslash
    tic(); x = C\(C'\b); toc()
    norm(A*x-b,1)/norm(b) 
    // solving the 2 triangular system with solve
    tic(); x = solve(C, solve(C,b,mode="upT"), mode="up"); toc()
    norm(A*x-b,1)/norm(b)
  \end{mintednsp}

\end{examples}

% -- Authors
\begin{authors}
  interface by Jean-Philippe Chancelier and Bruno Pincon. Internal use of lapack 
  routines described above.
\end{authors}
