% -*- mode: latex -*-
%% Scilab ( http://www.scilab.org/ ) - This file is part of Scilab
%% Copyright (C) 1987-2016 - F. Delebecque
%%
%% This program is free software; you can redistribute it and/or modify
%% it under the terms of the GNU General Public License as published by
%% the Free Software Foundation; either version 2 of the License, or
%% (at your option) any later version.
%%
%% This program is distributed in the hope that it will be useful,
%% but WITHOUT ANY WARRANTY; without even the implied warranty of
%% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
%% GNU General Public License for more details.
%%
%% You should have received a copy of the GNU General Public License
%% along with this program; if not, write to the Free Software
%% Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307  USA
%%                                                                                                

\mansection{svd}
\begin{mandesc}
  \short{svd}{singular value decomposition} \\ % 
\end{mandesc}
%\index{svd}\label{svd}
%-- Calling sequence section
\begin{calling_sequence}
\begin{verbatim}
  S=svd(X,tol=tol,mode= str)  
  [U,S,V,rk]=svd(X,tol=tol,mode= str)  
\end{verbatim}
\end{calling_sequence}
%-- Parameters
\begin{parameters}
  \begin{varlist}
    \vname{X}: a real or complex matrix.
    \vname{tol}: a real number.
    \vname{mode}: a string which can be \verb!''! or \verb!'e'!
    \vname{S}: a real vector giving the singular values.
    \vname{U,V}: orthogonal or unitary square matrices (singular vectors).
  \end{varlist}
\end{parameters}
\begin{mandescription}
  \verb![U,S,V] = svd(X)! produces a real vector \verb!S!, of dimension 
  \verb!min(size(X))! with elements in decreasing order, and unitary matrices
  \verb!U! and \verb!V! so that \verb!X = U*S1*V'! where 
  \verb!S1=zeros(size(X));S1.set_diag[S,0]!. 
  
  When the optional argument \verb!mode! is given and set to \verb!'e'! 
  the function returns an "economy size" decomposition. 
  If \verb!X! is a m-by-n matrix with \verb!m > n! (resp. \verb!m < n!) 
  then only the first \verb!n! (resp. \verb!m!) 
  columns of \verb!U! (resp. of \verb!V!) are computed. 

  \verb!rk! gives in addition the numerical rank of \verb!X! i.e. the number of
  singular values larger than \verb!tol*S(1)!. The default value of \verb!tol!  is
  the same as in \verb!rank! and it can be given throught the optional argument
  \verb!tol!.
\end{mandescription}
%--example 
\begin{examples}
  \begin{mintednsp}{nsp}
    X=rand(4,2)*rand(2,4)
    s= svd(X)
    sqrt(spec(X*X'))
    [U,S,V,rk]=svd(X);
    S1=zeros(size(X));S1.set_diag[S,0];
    norm(U*S1*V' - X)
  \end{mintednsp}
  \begin{mintednsp}{nsp}
    X=rand(4,7);
    [U,S,V]=svd(X,mode='e');
    norm(U*diag(S)*V' -X) 
  \end{mintednsp}
  \begin{mintednsp}{nsp}
    X=rand(7,4);
    [U,S,V]=svd(X,mode='e');
    norm(U*diag(S)*V' -X) 
  \end{mintednsp}
\end{examples}
%-- see also
\begin{manseealso}
  \manlink{rank}{rank} \manlink{qr}{qr} \manlink{colcomp}{colcomp} \manlink{rowcomp}{rowcomp} \manlink{sva}{sva} \manlink{spec}{spec}  
\end{manseealso}

