% -*- mode: latex -*-

\mansection{Cells}
\begin{mandesc}
  \short{Cells}{matrix of nsp objects data type}
\end{mandesc}
% -- Calling sequence section
\begin{calling_sequence}
\begin{verbatim}
A={a11, a12, ..., a1n;
   a21, a22, ..., a2n;
   ...
   am1, am2, ...; amn}
A = cell(m, n)   // preallocation
\end{verbatim}
\end{calling_sequence}
% -- Parameters
\begin{parameters}
  \begin{varlist}
    \vname{a11 ...}: nsp objects
    \vname{m, n}: integers (dimensions of the cells array)
  \end{varlist}
\end{parameters}

\begin{mandescription}

The \emph{Cells} data type is used to create matrix of nsp objects. 
In the current implementation, cell arrays are two dimensional arrays. 

column cell vectors are considered as \verb!m x 1! matrices and row cell vectors
as \verb!1 x n! matrices.

Internally \emph{Cells} type are stored by default as a unidimensional array of \emph{Objects},
It is therefore always possible to access elements with one index assuming a column order 
storage. 
\end{mandescription}

\paragraph{Operations on Cells}
\itemdesc{Cells methods}
\begin{itemize}
\item \verb+[bool,i,j]=C.has[Obj]+ returns true if \verb+Obj+ is present in the cell array \verb+C+ and if requested also returns indices. 
  Presence is checked via the equal operator i.e true is returned if \verb+C{i,j}.equal[Obj]+.
\end{itemize}
\itemdesc{Methods from the matint interface}
\begin{itemize}
\item \verb+A.redim[m,n]+ reshape matrix to size \verb+m+x\verb+n+. \verb+m+ or \verb+n+ can be set to \verb+-1+ 
\item \verb+A.concatr[B]+ \verb+A = [A,B]+
\item \verb+A.concatd[B]+ \verb+A = [A;B]+
\item \verb+A.perm_elem[p,q,dim]+ permute values, rows (\verb+dim=1+) or columns (\verb+dim=2+).
\item \verb+A.set_diag[B [,k]]+ sets the \verb+k+-th diagonal of cell array \verb+A+ to \verb+B+.
\item \verb+A.enlarge[m,n]+ sets the size of \verb+A+ to \verb+(Max(m,size(A,'r')),Max(n,size(A,'c')))+ and fill 
  added elements with default value.
\end{itemize}

\itemdesc{Extraction, insertion, deletion}
For \emph{Cells} data type, operations performed with \verb+{.}+ operate on the stored objects whereas 
operation performes with \verb+(.)+ operate on \emph{Cells} data type. For example, if \verb+C={5,6}+, 
\verb+C(1,1)+ will return a \verb+1x1+ \emph{Cells} whereas  \verb+C{1,1}+ will return the numeric matrix \verb+5+. 

In the sequel, \verb+I+ and \verb+J+ are matrices giving indices. Thus, \verb+I+ and \verb+J+ are 
numeric or boolean matrices the can also be set to \verb+:+ in that case they stand for the whole 
element, or row ,or column indices of the matrix. 

\begin{itemize}
\item \verb+A(I,J)+ is a new cell array build from \verb+A+ with entries in \verb+I+ and \verb+J+. 
\item \verb+A(I,:)+ is a new cell array build from \verb+A+ with row indices in \verb+I+.
\item \verb+A(:,J)+ is a new cell array build from \verb+A+ with column indices in \verb+I+.
\item \verb+A(:,:)+ is \verb+A+
\item \verb+A(:)+ is a new cell array obtained by stacking the columns of \verb+A+.
\item Note that a unique indices vector can be used using the column order storage.
\end{itemize}

\begin{itemize}
\item \verb+A(I,J)=B+ is only valid if \verb+B+ is of \emph{Cells} type. 
  it inserts cell array \verb+B+ into cell array \verb+A+ in rows \verb+I+ and columns \verb!J!.
  The dimensions of \verb!B! must match with dimensions of a \verb+length(I)xlength(J)+ cell array 
  (which means that \verb!B! can be a \verb!1x1! cell array or be of dimension \verb+length(I)xlength(J)+. 
\item A special case appears when \verb!B! is an empty cell array. In that case the sub cell array of 
  \verb!A! specified by \verb+IxJ+ is removed and the matrix is reshaped to a column array when the deletion 
  operation is not consistent with original dimension. For example \verb+A(:,J)={}+ removes the columns 
  of \verb+A+ with indices in \verb+J+. \verb!A(3,3)={}! removes element \verb!(3,3)! and reshape
  the array to a column array.
\end{itemize}

\begin{itemize}
\item \verb+A{I,J}=...+ fills the entries of cell array \verb+A+ in rows \verb+I+ and columns \verb!J! 
  with the right hand side values of the affectation sign. The values are of course stored using the 
  column order storage. The size of the cell array \verb+A+ can grow according to rows and columns indices. 
  For example if \verb+A={1,5}+ and we use \verb+A{2:3,1:2}=(1,2,3,4)+ then \verb!A! will be a \verb!3x2! cell 
  array.
\item \verb+A{I,J}+ returns \verb+length(I)xlength(J)+ objects on the calling stack extracted from 
  \verb!A!. For example if \verb+A={[1,2],[5;6]}+ then \verb+[x,y]=A{1:2}+ will store \verb+[1,2]+ in 
  \verb+x+ and \verb+[5;6]+ in \verb+y+.
\verb Insertion and extraction can of course be recursively called on the cell array elements by chaining 
  operator \verb+{.}+ or \verb+(.)+ as for example in \verb!A={4,5};A{2}(3,4)=45!. 
%Note that 
% in nsp the path to an element of a recursive object can also be specified using a list. For example 
% if \verb+A={1,{5,6}}+ then \verb+A{2}{1}(3,3)=56+ can also be performed by \verb+A{list(2,1)}(3,3)=56+.
\end{itemize}

\itemdesc{Empty cells}
Empty cells are \emph{Cells} with zero rows or zero columns. Operations with empty cells
are compatible with linear algebra operations. 

\itemdesc{For loop control}
Let \verb+A+ be a \emph{Cells} object~:
\begin{verbatim}
     for col=A
       ....
     end
\end{verbatim} 
is a loop with $size(A,2)$ iterations, the loop 
variable  \verb+col+ being set to the ith column of \verb+A+ at the \verb!i!-th iteration.

\itemdesc{Some functions}
\begin{itemize}
   \item \verb+unique(C)+ eliminate redundancies (in the equal sense) in cell array elements. 
   \item \verb+ce2m(C,indice=i,notm=val1,noti=val2)+ converts a cell array to numeric matrix
     with the following conventions if a \verb+C+ entry is not a numeric matrix then \verb!val1! is inserted 
     (default value \verb!%nan!). If \verb+C+ entry is a numeric matrix then entry \verb!i! of the matrix 
     is extracted (default value \verb!1!) and if index \verb!i! does not exists then \verb!val2! is inserted.
     \index{ce2m}\label{ce2m}
   \item \verb+C=m2ce(M [,rows,cols])+ converts a matrix to a cell array \verb+rows+ and \verb+cols+ giving the 
     partition of the matrix. When \verb+rows+ and \verb+cols+ are not given the matrix is partitioned into \verb!1x1! 
     matrices.
     \index{m2ce}\label{m2ce}
   \item \verb+map(C,f [,args])+ maps the function \verb!f! to each element of the cell array \verb!C! returning 
     a new cell array.
     \index{map}\label{map}
\end{itemize}

\begin{examples}
\begin{itemize}
\item Creation, extraction, insertion with \verb+{.}+:
\begin{mintednsp}{nsp}
  M=rand(4,4);
  A={8,9,M,"nsp"};  
  b=A{1} 	
  [a,b]=A{[1,3]};
  A{1:2}=(M,78) ; 
  A{:} = (4,5,6,7); 
  A={8,9;M,"nsp"};  
  A{1:2,1}=(56,67);
  A{1:2,1:2}=(1,2,3,4);
  A{3}=8;
\end{mintednsp}

\item Using \verb+{.}+ to provide a sequence of arguments to a function
\begin{mintednsp}{nsp} 
  function y=f(varargin);y=length(varargin);endfunction;
  A={8,9,M,"nsp"}; // creation 
  f(A{:})
\end{mintednsp}
\item Creation, extraction, insertion with \verb+(.)+:
\begin{mintednsp}{nsp}
  A={}; 
  A([1,3]) = {7,8} // affectation 
  A([1:3]) // extraction of a sub cell array
  A(1,2) = {89};  // same result as A{1,2} = 89;
  A={1,2;3,4}
  { A{:,1}}   // 1x2 
  A(:,1)      // 2x1 
\end{mintednsp}

\item using \verb+map+:
\begin{mintednsp}{nsp}
  A={7,8,rand(4,6),'foo'}; 
  function y=len(x);y=length(x);endfunction;
  Res=map(A,len);
  function y=plus_val(x,args);y=x+args(1);endfunction;
  Res=map({7,8,rand(2,2)},plus_val,list(45))
\end{mintednsp}

\item using \verb!ce2m! and \verb!m2ce!

\begin{mintednsp}{nsp}
  A=testmatrix('magic',5);
  C=m2ce(A,[1,2,5],[1,3,6]);

  A=1:10;
  C=m2ce(A,[1,2],1:11);
  
  C=cell(1,10);
  for i=1:10 
    C{i}=rand(1,2);
  end 
  A1=ce2m(C);
  B1=ce2m(C,indice=5); 
  C{1} = 'magic'
  A1=ce2m(C,notm=%inf);
  
  A1=ce2m(C,indice=100,noti=67,notm=%inf);
\end{mintednsp}

\end{itemize}

\end{examples}

% -- Authors
\begin{authors}
  Jean-Philippe Chancelier
\end{authors}





