>> help audiodevinfo   
 AUDIODEVINFO Audio device information.
    DEVINFO = AUDIODEVINFO returns a structure DEVINFO containing two fields, 
    input and output.  Each of these fields is an array of structures, each 
    structure containing information about one of the audio input or output 
    devices on the system.  The individual device structure fields are Name 
    (name of the device, string), DriverVersion (version of the installed 
    device driver, string), and ID (the device's ID).
 
    AUDIODEVINFO(IO) returns the number of input or output audio devices on 
    the system.  Set IO = 1 for input, IO = 0 for output.
 
    AUDIODEVINFO(IO, ID) returns the name of the input or output audio device 
    with the given device ID.
 
    AUDIODEVINFO(IO, NAME) returns the device ID of the input or output audio 
    device with the given name (partial matching, case sensitive).  If no 
    audio device is found with the given name, -1 is returned.
 
    AUDIODEVINFO(IO, ID, 'DriverVersion') returns the driver version string of 
    the specified audio input or output device.
 
    AUDIODEVINFO(IO, RATE, BITS, CHANS) returns the device ID of the first 
    input or output device that supports, number of bits, 
    and number of channels specified in RATE, BITS, and CHANS, respectively.
    If no supportive device is found, -1 is returned.
 
    AUDIODEVINFO(IO, ID, RATE, BITS, CHANS) returns 1 or 0 for whether or not 
    the input or output audio device specified in ID can support the given 
    sample rate, number of bits, and number of channels.
 
    This function is only for use with Windows platforms.
 
    See also AUDIOPLAYER, AUDIORECORDER. 
