% -*- mode: latex -*-

\mansection{addinter}
\begin{mandesc}
  \short{link}{dynamic interface loader} 
\end{mandesc}
\index{addinter}\label{addinter}
%-- Calling sequence section
\begin{calling_sequence}
\begin{verbatim}
   addinter(library,libname)  
\end{verbatim}
\end{calling_sequence}
%-- Parameters
\begin{parameters}
  \begin{varlist}
    \vname{library}: contains the path of a shared library to be loaded 
    or the id of the library if it was previously loaded by \verb!link!.
    \vname{libname}:  Is a string giving the name of the nsp interface.
  \end{varlist}
\end{parameters}
\begin{mandescription}
  \verb!addinter! is used to dynamically add a set of functions in Nsp 
  by dynamically loading their interfaces. 
  The arguments given to \verb!addinter! are a shared library and the name of the function which gather all the interfaces. If the second argument 
  given to \verb!addinter! is \verb!'foo'!, then the entry \verb!foo_Interf! 
  will be searched in the dynamic library described by the argument \verb!library!. If \verb!addinter! succeed then \verb!foo_Interf! will appear in 
  the entry listed by \verb!link('show')! and \verb!c_link('foo_Interf')! 
  will return \verb!%t!. 
  This function is often used in conjunction with the function 
  \verb!ilib_build'! which is used to build the shared library and 
  to produce a script containing the call to \verb!addinter!.
\end{mandescription}
%-- see also
\begin{manseealso}
  \manlink{link}{link} 
  \manlink{c\_link}{c_link}
  \manlink{ilib\_build}{ilib_link}
  \manlink{ulink}{ulink}
\end{manseealso}

