% -*- mode: latex -*-
\mansection{exists}
\begin{mandesc}
  \short{exists}{checks for variables}
\end{mandesc}
% -- Calling sequence section
\begin{calling_sequence}
\begin{verbatim}
  bool= exists(name [, str])  
\end{verbatim}
\end{calling_sequence}
%-- Parameters
\begin{parameters}
  \begin{varlist}
    \vname{name}: a string giving the symbol name to be searched.
    \vname{where}: an optional character string which should be chosen 
    among \verb+'all'+, \verb+'caller'+, \verb+'callers'+, \verb+'local'+,
    \verb+'global'+, \verb+'function'+, \verb+'nsp-function'+, or 
    \verb+'callable'+.
    \verb{bool} a boolean. 
  \end{varlist}
\end{parameters}
\begin{mandescription}
  This function can be used to search for symbols, it returns true if 
  symbol names \verb+name+ is found and false if not. 
  \begin{varlist}
    \vname{'all'}: this is the default value, which  means \verb+local+ or 
    \verb+callers+ or \verb+global+.
    \vname{'caller'}:  search in the caller. 
    \vname{'callers'}: search in the calling stack frames.
    \vname{'local'}: search in the local fram.
    \vname{'global'}: search in the global frame.
    \vname{'function'}: search in primitives. 
    \vname{'nsp-function'}: search in libraries of nsp coded functions.
    \vname{'callable'}: means \verb+function+ or \verb+nsp-function+.
  \end{varlist}
\end{mandescription}
%--example 
\begin{examples}
  \begin{Verbatim}
    global x1;
    x1 = 1;
    x2 = 2;
    function y=f(s,env); x4=4;y=exists(s,env);endfunction;
    function y=g(s,env); x3=3; y=f(s,env);endfunction;
    // net calls should return true.
    y=g('x4','local')
    y=g('x3','caller')
    y=g('x2','callers')
    y=g('x1','callers')
    y=g('x1','global')
    // functions 
    exists('sin_m','function')
  \end{Verbatim}
\end{examples}
%-- see also
\begin{manseealso}
  \manlink{acquire}{acquire} 
\end{manseealso}
