% -*- mode: latex -*-

\mansection{ilib\_build}
\begin{mandesc}
  \shortunder{ilib\_build}{ilib_build}{utility for toolboxes interfaces}
\end{mandesc}
%-- Calling sequence section
\begin{calling_sequence}
\begin{verbatim}
  ilib_build(libname,table,files,libs [,makename,ldflags,cflags,fflags])  
\end{verbatim}
\end{calling_sequence}
%-- Parameters
\begin{parameters}
  \begin{varlist}
    \vname{libname}: a string giving the name of the library to be build. This name 
    should start with \verb!lib!.
    \vname{table}: a string matrix which can have two or three column. 
    The first column gives nsp function name, the second column gives the name of 
    the interface which is used to implement the function given in column one, and the 
    third column which is optional gives the type of interface used.  
    Values for the third column entries are to be chosen among 
    \begin{itemize}
      \item 'cmex', 'fmex', 'Fmex': when the interface is implemented 
        using mex files (C or Fortran)
      \item 'cnsp', 'csci', 'fsci', 'fnsp': when the interface is a Nsp standard interface.
      \item 'direct': for direct interface. 
    \end{itemize}
    \vname{files}: a string matrix giving objects files needed for the shared library creation.
    \vname{libs}:  a string matrix giving extra shared libraries needed to solve references 
    for the shared library to be build.
    \vname{makename}: a string giving the name of the Makefile file to be generated.
    \vname{ldflags,cflags,fflags}: strings giving options for the linker, and the C or 
    Fortran compilers.
  \end{varlist}
\end{parameters}
\begin{mandescription}
  \verb!ilib_build! is used to facilitate the creation of a shared libraries 
  which contains a set of interface for Nsp new functions. It generates 
  a loader file which can be used to dynamically load the shared library 
  into Nsp. Many examples are provided in the \verb!tests/addinter! 
  directory.
\end{mandescription}
%--example 
\begin{examples}
  A small example with just one function added. The function 
  is named \verb!fun1! and its interface is \verb!int_fun1!.
  \begin{Verbatim}
    code = ['#include <math.h>'
            '#include <stdlib.h>'
            '#include <string.h>'
            '#include <nsp/interf.h>'
            ''
            'int int_fun1(Stack stack, int rhs, int opt, int lhs)'
            '{'
              'NspMatrix *B,*C;'
              'CheckRhs(1,1);'
              'CheckLhs(1,1);'
              'if ((B=GetMatCopy(stack,1))== NULLMAT ) return RET_BUG;'
              'if ((C=nsp_matrix_copy(B))== NULLMAT ) return RET_BUG;'
              'nsp_mat_sin(B); /* B <-- sin(B) **/'
              'nsp_mat_cos(C);'
              'if (nsp_mat_dadd(B,C) == FAIL) return RET_BUG;'
              'nsp_matrix_destroy(C);'
              'NSP_OBJECT(B)->ret_pos = 1;'
              'return 1;'
            '}'];
    fd = fopen('fun1.c',mode="w");
    fd.put_smatrix[code];
    fd.close[];
    files=['fun1.o'];
    ilib_build('libfoo',['fun1','int_fun1'],files,[]);
    // load the shared library 
    exec loader.sce 
    //using the new primitive 
    x=67;
    fun1(x)<>sin(x)+cos(x)
  \end{Verbatim}
\end{examples}
%-- see also
\begin{manseealso}
  \manlink{addinter}{addinter}
  \manlink{link}{link} 
\end{manseealso}

