% -*- mode: latex -*-

\mansection{ilib\_for\_link}
\begin{mandesc}
  \shortunder{ilib\_for\_link}{ilib_for_link}{utility for dynamic library management}\\
\end{mandesc}
\index{ilib\_for\_link}\label{ilib-for-link}
%-- Calling sequence section
\begin{calling_sequence}
\begin{verbatim}
  ilib_for_link(names,files,libs,flag [
         ,makename=,loadername=,libname=,ldflags=,cflags=,fflags=,cc=]);
\end{verbatim}
\end{calling_sequence}
%-- Parameters
\begin{parameters}
  \begin{varlist}
    \vname{names} : a string matrix giving the entry names which are to be linked.
    \vname{files} : a string matrix giving objects files needed for shared library creation. 
    Note that the suffix to use for object files is \verb+.o+ on all operating systems. 
    \vname{libs} : a string matrix giving extra libraries needed for shared library creation
    \vname{flag} : a string flag ("c" or "f") for C or Fortran entry points.
    \vname{makename} : a string giving the name of the Makefile to be generated  (default value \verb!Makelib!).
    \vname{loadername} : a string giving the name of the loader file to be generated (default value  \verb!loader.sce!).
    \vname{libname} : a string giving the name of the dynamic library to be generated (default value is build from the first 
    given file name in \verb!files!).
    \vname{ldflags}: optional string to be given to the linker.
    \vname{cflags}: optional string to be given to the C/C++ compiler.
    \vname{fflags}: optional string to be given to the Fortran compiler.
    \vname{cc}: optional string to give the C compiler name.
  \end{varlist}
\end{parameters}
\begin{mandescription}
  \verb!ilib_for_link! can be used to build a dynamic library from a set of given files 
  and to obtain a script which contains a proper call to nsp function \verb!link! for loading 
  the shared library ane add entry points given by \verb!names! to nsp. The advantage of this
  script comes from the fact that the compilation and link process can be achieved from nsp 
  for all the supported operating systems. The script \verb!ilib_for_link! will generate a
  makefile (whose name is given by \verb!makename!) which can be used directly to compile 
  the dynamic library. 
\end{mandescription}
%--example 
\begin{examples}
  \begin{program}
    f1=['int ext1c(n, a, b, c)'
         'int *n;     double *a, *b, *c;'
         '{int k;'
         '  for (k = 0; k $<$ *n; ++k) '
         '      c[k] = a[k] + b[k];'
         '  return(0);}'];
    mputl(f1,'fun1.c')
    //creating the shared library (a gateway, a Makefile and a loader are 
    //generated. 
    ilib_for_link('ext1c','fun1.o',[],"c") 
    // load the shared library 
    exec loader.sce 
    //using the new primitive
    a=[1,2,3];b=[4,5,6];n=3;
    c=call('ext1c',n,1,'i',a,2,'d',b,3,'d','out',[1,3],4,'d');
    if norm(c-(a+b)) $>$ %eps then pause,end
  \end{program}
\end{examples}
%-- see also
\begin{manseealso}
  \manlink{link}{link} 
  \manlink{ulink}{ulink}
  \manlink{c\_link}{c-link}
\end{manseealso}

