% -*- mode: latex -*-
\mansection{load}
\begin{mandesc}
  \short{load}{load saved objects}
  \short{sci_load}{load objects which were saved by scicoslab}
\end{mandesc}

  %-- Calling sequence section
\begin{calling_sequence}
  \begin{verbatim}
    load(filename [, names]);
    H= load(filename [, names] );
    sci_load(filename [, name1,...,namen])  
    H=sci_load(filename [,name1,...,namen]);
  \end{verbatim}
\end{calling_sequence}
%-- Parameters
\begin{parameters}
  \begin{varlist}
    \vname{filename}: a string giving a file pathname.
    \vname{namei}: strings specifying object names. 
    \vname{names}: a string matrix specifying object names. 
  \end{varlist}
\end{parameters}
\begin{mandescription}
  The \verb!load! command is used to reload in the running nsp context 
  objects previously saved in a file by the \verb!save! command. 
  If the function is called with only one argument then the 
  whole file content is reloaded. If a string matrix \verb!names! is given then 
  objects with corresponding names are searched and if found reloaded in 
  the running nsp session. 
  If a left hand side argument is provided then an hash table 
  filled with the loaded values is returned.
  
  The \verb!sci_load! command is used to reload in the running nsp context
  objects previously saved by scicoslab (or saved with the  \verb!sci_save! 
  commande). If a left hand side argument is provided then an hash table 
  filled with the loaded values is returned.
\end{mandescription}
%--example 
\begin{examples}
  \begin{mintednsp}{nspxxx}
a=rand(2,2);
    save('foo.dat',a,b=ones(4,2));
    clear a,b;
    load('foo.dat');
    H=load('foo.dat');
    H=load('foo.dat','a');
  \end{mintednsp}
\end{examples}
%-- see also
\begin{manseealso}
  \manlink{save}{save} 
\end{manseealso}

