% -*- mode: latex -*-
\mansection{csim}
\begin{mandesc}
  \short{csim}{simulation (time response) of linear system} \\ % 
\end{mandesc}
%\index{csim}\label{csim}
%-- Calling sequence section
\begin{calling_sequence}
\begin{verbatim}
  [y [,x]]=csim(u,t,sl,[x0 [,tol]])  
\end{verbatim}
\end{calling_sequence}
%-- Parameters
\begin{parameters}
  \begin{varlist}
    \vname{u}: function, list or string (control)
    \vname{t}: real vector specifying times with, \verb!t(1)! is the initial
    time (\verb!x0=x(t(1))!).
    \vname{sl}: list (\verb!syslin!)
    \vname{y}: a  matrix such that   \verb!y=[y(t(i)]!, i=1,..,n
    \vname{x}: a  matrix such that   \verb!x=[x(t(i)]!, i=1,..,n
    \vname{tol}: a 2 vector [atol rtol] defining absolute and relative
    tolerances for ode solver (see ode)
  \end{varlist}
\end{parameters}
\begin{mandescription}

  simulation of the controlled linear system \verb!sl!.  \verb!sl! is assumed to
  be a continuous-time system represented by a \verb!syslin! list.\verb!u! is
  the control and \verb!x0! the initial state.\verb!y! is the output and
  \verb!x! the state.
  The control can be:
  \begin{itemize}
  \item a function: \verb![inputs]=u(t)!
  \item a list: \verb!list(ut,parameter1,....,parametern)! such that:
    \verb!inputs=ut(t,parameter1,....,parametern)! (\verb!ut! is a function)
  \item the string \verb!"impuls"! for impulse response calculation
    (here \verb!sl! is assumed SISO without direct feed through and \verb!x0=0!)
  \item the string \verb!"step"! for step response calculation 
    (here \verb!sl! is assumed SISO without direct feed-through and
    \verb!x0=0!)
  \item a vector giving the values of u correponding to each t value.
  \end{itemize}
\end{mandescription}
%--example 
\begin{examples}
  \begin{mintednsp}{nsp}
    s=poly(0,'s');w=ssrand(1,1,3);w.A = w.A-2*eye(size(w.A));
    t=0:0.05:5;
    //impulse(w) = step (s * w)
    xbasc(0);xset("window",0);xselect();
    plot2d([t',t'],[(csim('step',t,tf2ss(s)*w))',0*t'])
    xbasc(1);xset("window",1);xselect();
    plot2d([t',t'],[(csim('impulse',t,w))',0*t'])
    //step(w) = impulse (s^-1 * w)
    xbasc(3);xset("window",3);xselect();
    plot2d([t',t'],[(csim('step',t,w))',0*t'])
    xbasc(4);xset("window",4);xselect();
    plot2d([t',t'],[(csim('impulse',t,tf2ss(1/s)*w))',0*t'])
    //input defined by a time function
    function u=input(t);u=abs(sin(t));endfunction;
    xbasc();plot2d([t',t'],[(csim(input,t,w))',0*t'])
  \end{mintednsp}
\end{examples}
%-- see also
\begin{manseealso}
  \manlink{syslin}{syslin} \manlink{dsimul}{dsimul} \manlink{flts}{flts} \manlink{ltitr}{ltitr} \manlink{rtitr}{rtitr} \manlink{ode}{ode} \manlink{impl}{impl}  
\end{manseealso}
