% -*- mode: latex -*-
\mansection{lqe}
\begin{mandesc}
  \short{lqe}{linear quadratic estimator (Kalman Filter)  } \\ % 
\end{mandesc}
% \index{lqe}\label{lqe}
% -- Calling sequence section
\begin{calling_sequence}
\begin{verbatim}
  [K,X]=lqe(P21)   
\end{verbatim}
\end{calling_sequence}
% -- Parameters
\begin{parameters}
  \begin{varlist}
    \vname{P21}: \verb!syslin! list
    \vname{K, X}: real matrices
  \end{varlist}
\end{parameters}
\begin{mandescription}
  \verb!lqe! returns the Kalman gain for the filtering
  problem in continuous or discrete time.\verb!P21! is a \verb!syslin! list representing the system \verb!P21=[A,B1,C2,D21] P21=syslin('c',A,B1,C2,D21) or P21=syslin('d',A,B1,C2,D21)!
  The input to \verb!P21! is a white noise with variance:
\begin{verbatim}
  [B1 ]               [Q  S]
  BigV=[   ] [ B1' D21'] = [    ]
  [D21]               [S' R]
\end{verbatim}
  \verb!X! is the solution of the stabilizing Riccati 
  equation and \verb!A+K*C2! is stable.
  In continuous time:
\begin{verbatim}
  (A-S*inv(R)*C2)*X+X*(A-S*inv(R)*C2)'-X*C2'*inv(R)*C2*X+Q-S*inv(R)*S'=0
\end{verbatim}
\begin{verbatim}
  K=-(X*C2'+S)*inv(R)
\end{verbatim}
  In discrete time:
\begin{verbatim}
  X=A*X*A'-(A*X*C2'+B1*D21')*pinv(C2*X*C2'+D21*D21')*(C2*X*A'+D21*B1')+B1*B1'
\end{verbatim}
  \verb!K=-(A*X*C2'+B1*D21')*pinv(C2*X*C2'+D21*D21')!\verb!xhat(t+1)= E(x(t+1)| y(0),...,y(t))! (one-step predicted \verb!x!)
  satisfies the recursion:
\begin{verbatim}
  xhat(t+1)=(A+K*C2)*xhat(t) - K*y(t).
\end{verbatim}
\end{mandescription}
% --example 
\begin{examples}
  \begin{mintednsp}{nsp}
    //Assume the equations
    //.
    //x = Ax + Ge
    //y = Cx + v
    //with
    //E ee' = Q_e,    Evv' = R,    Eev' = N 
    //
    //This is equivalent to
    //.
    //x = Ax  + B1 w
    //y = C2x + D21 w
    //with E {[Ge ]  [Ge v]' } = E {[B1w ] [B1w D21w]' } = bigR =
    //        [ v ]                 [D21w]    
    //
    // [B1*B1'  B1*D21';
    // D21*B1'  D21*D21']  
    //=
    //[G*Q_e*G' G*N;
    // N*G' R]
    // 
    //To find (B1,D21) given (G,Q_e,R,N) form bigR =[G*Q_e*G' G*N;N'*G' R].
    //Then [W,Wt]=fullrf(bigR);  B1=W(1:size(G,1),:);
    //D21=W(($+1-size(C2,1)):$,:)
    //
    //P21=syslin('c',A,B1,C2,D21);
    //[K,X]=lqe(P21);
    //Example:
    nx=5;ne=2;ny=3;
    A=-diag(1:nx);G=ones(nx,ne);
    C=ones(ny,nx); Q_e(ne,ne)=1; R=diag(1:ny); N=zeros(ne,ny);
    bigR =[G*Q_e*G' G*N;N'*G' R];
    [W,Wt]=fullrf(bigR);B1=W(1:size(G,1),:);
    D21=W(($+1-size(C,1)):$,:);
    C2=C;
    P21=syslin('c',A,B1,C2,D21);
    [K,X]=lqe(P21);
    //Riccati check:
    S=G*N;Q=B1*B1';
    (A-S*inv(R)*C2)*X+X*(A-S*inv(R)*C2)'-X*C2'*inv(R)*C2*X+Q-S*inv(R)*S'
    //Stability check:
    spec(A+K*C)
  \end{mintednsp}
\end{examples}
% -- see also
\begin{manseealso}
  \manlink{lqr}{lqr} \manlink{observer}{observer}  
\end{manseealso}
% -- Author
\begin{authors}
  F. D.   
\end{authors}
