% -*- mode: latex -*-
\mansection{lqg2stan}
\begin{mandesc}
  \short{lqg2stan}{LQG to standard problem} \\ % 
\end{mandesc}
% \index{lqg2stan}\label{lqg2stan}
% -- Calling sequence section
\begin{calling_sequence}
\begin{verbatim}
  [P,r]=lqg2stan(P22,bigQ,bigR)  
\end{verbatim}
\end{calling_sequence}
%-- Parameters
\begin{parameters}
  \begin{varlist}
    \vname{P22}: \verb!syslin! list (nominal plant) in state-space form
    \vname{bigQ}: \verb![Q,S;S',N]! (symmetric) weighting matrix
    \vname{bigR}: \verb![R,T;T',V]! (symmetric) covariance matrix
    \vname{r}: \verb!1!x\verb!2! row vector = (number of measurements, number of inputs)  (dimension of  the 2,2 part of \verb!P!)
    \vname{P}: \verb!syslin! list (augmented plant)
  \end{varlist}
\end{parameters}
\begin{mandescription}
  \verb!lqg2stan!  returns the augmented plant for linear LQG (H2) controller 
  design.\verb!P22=syslin(dom,A,B2,C2)! is the nominal plant; it can be in continuous 
  time (\verb!dom='c'!) or discrete time (\verb!dom='d'!).
\begin{verbatim}
  . 
  x = Ax + w1 + B2u
  y = C2x + w2
\end{verbatim}
for continuous time plant.
\begin{verbatim}
  x[n+1]= Ax[n] + w1 + B2u
  y = C2x + w2
\end{verbatim}
for discrete time plant.
The (instantaneous) cost function is \verb![x' u'] bigQ [x;u]!.
The covariance of \verb![w1;w2]! is \verb!E[w1;w2] [w1',w2'] = bigR!
If \verb![B1;D21]! is a factor of \verb!bigQ!, \verb![C1,D12]!
is a factor of \verb!bigR! and \verb![A,B2,C2,D22]! is
a realization of P22, then \verb!P! is a realization of
\verb![A,[B1,B2],[C1,-C2],[0,D12;D21,D22]!.
  The (negative) feedback computed by \verb!lqg! stabilizes \verb!P22!,
  i.e. the poles of \verb!cl=P22/.K! are stable.
\end{mandescription}
%--example 
\begin{examples}
  \begin{mintednsp}{nsp}
    ny=2;nu=3;nx=4;
    P22=ssrand(ny,nu,nx);
    bigQ=rand(nx+nu,nx+nu);bigQ=bigQ*bigQ';
    bigR=rand(nx+ny,nx+ny);bigR=bigR*bigR';
    [P,r]=lqg2stan(P22,bigQ,bigR);K=lqg(P,r);  //K=LQG-controller
    spec(h_cl(P,r,K))      //Closed loop should be stable
    //Same as Cl=P22/.K; spec(Cl('A'))
    s=poly(0,'s')
    lqg2stan(1/(s+2),eye(2,2),eye(2,2))
  \end{mintednsp}
\end{examples}
%-- see also
\begin{manseealso}
  \manlink{lqg}{lqg} \manlink{lqr}{lqr} \manlink{lqe}{lqe} \manlink{obscont}{obscont} \manlink{h\_inf}{h-inf} \manlink{augment}{augment} \manlink{fstabst}{fstabst} \manlink{feedback}{feedback}  
\end{manseealso}
%-- Author
\begin{authors}
  F.D.  
\end{authors}
