% -*- mode: latex -*-
\mansection{observer}
\begin{mandesc}
  \short{observer}{observer design} \\ % 
\end{mandesc}
%\index{observer}\label{observer}
%-- Calling sequence section
\begin{calling_sequence}
\begin{verbatim}
  Obs=observer(Sys,J)  
  [Obs,U,m]=observer(Sys [,flag,alfa])  
\end{verbatim}
\end{calling_sequence}
%-- Parameters
\begin{parameters}
  \begin{varlist}
    \vname{Sys}: \verb!syslin! list (linear system)
    \vname{J}: nx x ny constant matrix (output injection matrix)
    \vname{flag}: character strings (\verb!'pp'! or \verb!'st'! (default))
    \vname{alfa}: location of closed-loop poles (optional parameter, default=-1)
    \vname{Obs}: linear system (\verb!syslin! list), the observer
    \vname{U}: orthogonal matrix (see \verb!dt_ility!)
    \vname{m}: integer (dimension of unstable unobservable (\verb!st!)  or unobservable  (\verb!pp!) subspace)
  \end{varlist}
\end{parameters}
\begin{mandescription}
  \verb!Obs=observer(Sys,J)! returns the observer 
  \verb!Obs=syslin(td,A+J*C,[B+J*D,-J],eye(A))! obtained from \verb!Sys! 
  by a \verb!J! output injection. (td is the time domain of \verb!Sys!).
  More generally, \verb!observer! returns in \verb!Obs! an observer for 
  the observable part of linear system 
  \verb!Sys!: \verb!dotx=A x + Bu, y=Cx + Du!  represented by a \verb!syslin! list.
  \verb!Sys! has \verb!nx! state variables, \verb!nu! inputs and \verb!ny! outputs.
  \verb!Obs! is a linear system with matrices \verb![Ao,Bo,Identity]!, 
  where \verb!Ao! is \verb!no x no!, \verb!Bo! is \verb!no x (nu+ny)!, \verb! Co! is
  \verb!no x no! and \verb!no=nx-m!.
  Input to \verb!Obs! is \verb![u,y]! and output of \verb!Obs! is:
  xhat=estimate of x modulo unobservable subsp. (case \verb!flag='pp'!)
  or
  xhat=estimate of x modulo unstable unobservable subsp. (case \verb!flag='st'!)
  case \verb!flag='st'!:
  z=H*x can be estimated with stable observer iff \verb!H*U(:,1:m)=0!
  and assignable poles of the observer are set to \verb!alfa(1),alfa(2),...!
  case \verb!flag='pp'!:
  z=H*x can be estimated with given error spectrum iff \verb!H*U(:,1:m)=0! 
  all poles of the observer are assigned and set to \verb!alfa(1),alfa(2),...!
  If H satifies the constraint: \verb!H*U(:,1:m)=0!  (ker(H) contains unobs-subsp.
  of Sys) one has H*U=[0,H2] and the observer for 
  z=H*x is H2*Obs with H2=H*U(:,m+1:nx) i.e. Co, the C-matrix of the
  observer for H*x, is Co=H2.
  In the particular case where the pair \verb!(A,C)! of \verb!Sys! is 
  observable, one has \verb!m=0! and the linear system \verb!U*Obs! (resp.
  \verb!H*U*Obs!) is an observer for \verb!x! (resp. \verb!Hx!). 
  The error spectrum is \verb!alpha(1),alpha(2),...,alpha(nx)!.
\end{mandescription}
%--example 
\begin{examples}
  \begin{mintednsp}{nsp}
    nx=5;nu=1;ny=1;un=3;us=2;Sys=ssrand(ny,nu,nx,list('dt',us,us,un));
    //nx=5 states, nu=1 input, ny=1 output, 
    //un=3 unobservable states, us=2 of them unstable.
    [Obs,U,m]=observer(Sys);  //Stable observer (default)
    W=U';H=W(m+1:nx,:);[A,B,C,D]=abcd(Sys);  //H*U=[0,eye(no,no)];
    Sys2=ss2tf(syslin('c',A,B,H))  //Transfer u--$>$z
    Idu=eye(nu,nu);Sys3=ss2tf(H*U(:,m+1:$)*Obs*[Idu;Sys])  
    //Transfer u--$>$[u;y=Sys*u]--$>$Obs--$>$xhat--$>$HUxhat=zhat  i.e. u--$>$output of Obs
    //this transfer must equal Sys2, the u--$>$z transfer  (H2=eye).
    //Assume a Kalman model
    //dotx = A x + B u + G w
    // y   = C x + D u + H w + v
    //with Eww' = QN, Evv' = RN, Ewv' = NN
    //To build a Kalman observer:
    //1-Form BigR = [G*QN*G'         G*QN*H'+G*NN;
    //               H*QN*G'+NN*G'   H*QN*H'+RN];
    //the covariance matrix of the noise vector [Gw;Hw+v]
    //2-Build the plant P21: dotx = A x + B1 e ; y = C2 x + D21 e 
    //with e a unit white noise.
    // [W,Wt]=fullrf(BigR);
    //B1=W(1:size(G,1),:);D21=W(($+1-size(C,1)):$,:);
    //C2=C;
    //P21=syslin('c',A,B1,C2,D21);
    //3-Compute the Kalman gain
    //L = lqe(P21);
    //4- Build an observer for the plant [A,B,C,D];
    //Plant = syslin('c',A,B,C,D);
    //Obs = observer(Plant,L);
    //Test example:
    A=-diag(1:4);
    B=ones(4,1);
    C=B'; D= 0; G=2*B; H=-3; QN=2;
    RN=5; NN=0;
    BigR = [G*QN*G'         G*QN*H'+G*NN;
      H*QN*G'+NN*G'   H*QN*H'+RN];
    [W,Wt]=fullrf(BigR);
    B1=W(1:size(G,1),:);D21=W(($+1-size(C,1)):$,:);
    C2=C;
    P21=syslin('c',A,B1,C2,D21);
    L = lqe(P21);
    Plant = syslin('c',A,B,C,D);
    Obs = observer(Plant,L);
    spec(Obs.A)
  \end{mintednsp}
\end{examples}
%-- see also
\begin{manseealso}
  \manlink{dt\_ility}{dt-ility} \manlink{unobs}{unobs} \manlink{stabil}{stabil}  
\end{manseealso}
%-- Author
\begin{authors}
  F.D.  
\end{authors}
