% -*- mode: latex -*-
\mansection{stabil}
\begin{mandesc}
  \short{stabil}{stabilization} \\ % 
\end{mandesc}
%\index{stabil}\label{stabil}
%-- Calling sequence section
\begin{calling_sequence}
\begin{verbatim}
  F=stabil(A,B,alfa)  
  K=stabil(Sys,alfa,beta)  
\end{verbatim}
\end{calling_sequence}
%-- Parameters
\begin{parameters}
  \begin{varlist}
    \vname{A}: square real matrix (\verb!nx x nx!)
    \vname{B}:  real matrix (\verb!nx x nu!)

    \vname{alfa, beta}: real or complex vector (in conjugate pairs) or real
    number.

    \vname{F}: real matrix (\verb!nx x nu!)

    \vname{Sys}: linear system (\verb!syslin! list) (\verb!m! inputs, \verb!p!
    outputs).

    \vname{K}: linear system (\verb!p! inputs, \verb!m! outputs)
  \end{varlist}
\end{parameters}
\begin{mandescription}
  \verb!F=stabil(A,B,alfa)! returns a gain matrix \verb!F! such that
  \verb!A+B*F! is stable if pair \verb!(A,B)! is stabilizable.  Assignable poles
  are set to \verb!alfa(1),alfa(2),...!.  If \verb!(A,B)! is not stabilizable a
  warning is given and assignable poles are set to \verb!alfa(1),alfa(2),...!.
  If \verb!alfa! is a number all eigenvalues are set to this \verb!alfa!
  (default value is \verb!alfa=-1!).\verb!K=stabil(Sys,alfa,beta)! returns
  \verb!K!, a compensator for \verb!Sys!  such that \verb!(A,B)!-controllable
  eigenvalues are set to \verb!alfa! and \verb!(C,A)!-observable eigenvalues are
  set to \verb!beta!.  All assignable closed loop poles (which are given by the
  eigenvalues of \verb!Aclosed=h_cl(Sys,K)! are set to \verb!alfa(i)!'s and
  \verb!beta(j)!'s.
\end{mandescription}
%--example 
\begin{examples}
  \begin{mintednsp}{nsp}
    // Gain:
    Sys=ssrand(0,2,5,list('st',2,3,3));
    A=Sys.A;B=Sys.B;F=stabil(A,B);
    spec(A) //2 controllable modes 2 unstable uncontrollable modes
    //and one stable uncontrollable mode
    spec(A+B*F) //the two controllable modes are set to -1.
    // Compensator:
    Sys=ssrand(3,2,5,list('st',2,3,3)); //3 outputs, 2 inputs, 5 states
    //2 controllables modes, 3 controllable or stabilizable modes.
    K=stabil(Sys,-2,-3);  //Compensator for Sys.
    spec(Sys.A)
    spec(h_cl(Sys,K))   //K Stabilizes what can be stabilized.
  \end{mintednsp}
\end{examples}
%-- see also
\begin{manseealso}
  \manlink{st\_ility}{st-ility} \manlink{contr}{contr} \manlink{ppol}{ppol}  
\end{manseealso}
