% -*- mode: latex -*-
\mansection{ui\_observer}
\begin{mandesc}
  \shortunder{ui\_observer}{ui_observer}{unknown input observer} \\ % 
\end{mandesc}
%\index{ui\_observer}\label{ui-observer}
%-- Calling sequence section
\begin{calling_sequence}
\begin{verbatim}
  [UIobs,J,N]=ui_observer(Sys,reject,C1,D1)  
  [UIobs,J,N]=ui_observer(Sys,reject,C1,D1,flag,alfa,beta)  
\end{verbatim}
\end{calling_sequence}
%-- Parameters
\begin{parameters}
  \begin{varlist}
    \vname{Sys}: \verb!syslin! list containing the matrices \verb!(A,B,C2,D2)!.
    \vname{reject}: integer vector, indices of inputs of \verb!Sys! which are unknown.
    \vname{C1}: real matrix
    \vname{D1}: real matrix. \verb!C1! and \verb!D1! have the same number of rows.
    \vname{flag}: string \verb!'ge'! or \verb!'st'! (default) or \verb!'pp'!.
    \vname{alfa}: real or complex vector (loc. of closed loop poles)
    \vname{beta}: real or complex vector (loc. of closed loop poles)
  \end{varlist}
\end{parameters}
\begin{mandescription}
  Unknown input observer.\verb!Sys: (w,u) --$>$ y! is a \verb!(A,B,C2,D2)!
  syslin linear system with two inputs w and u, w being the unknown input.  The
  matrices B and D2 of Sys are (implicitly) partitioned as: \verb!B=[B1,B2]! and
  \verb!D2=[D21,D22]!  with \verb!B1=B(:,reject)!  and \verb!D21=D2(:,reject)!
  where reject = indices of unknown inputs.  The matrices \verb!C1! and
  \verb!D1! define \verb!z = C1 x + D1 (w,u)!, the to-be-estimated output.  The
  matrix \verb!D1! is (implicitly) partitioned as \verb!D1=[D11,D12]!  with
  \verb!D11=D(:,reject)!  The data (Sys, reject,C1, D1) define a 2-input
  2-output system:
\begin{verbatim}
  xdot =  A x + B1  w + B2  u
  z = C1 x + D11 w + D12 u
  y = C2 x + D21 w + D22 u
\end{verbatim}
An observer \verb!(u,y) --$>$ zhat! is looked for the output z.\verb!flag='ge'! no stability constraints
\verb!flag='st'! stable observer    (default) 
\verb!flag='pp'! observer with pole placement
alfa,beta = desired location of closed loop poles  (default -1, -2)
J=y-output to x-state injection.
N=y-output to z-estimated output injection.
UIobs = linear system (u,y) --$>$ zhat such that:
The transfer function: (w,u) --$>$ z  equals the composed transfer function:
[0,I;        UIobs
  Sys]
(w,u) -----$>$ (u,y) -----$>$ zhat
i.e. transfer function of system {A,B,C1,D1} equals transfer function 
\verb!UIobs*[0,I; Sys]!
Stability (resp. pole placement) requires detectability
(resp. observability) of (A,C2).
\end{mandescription}
%--example 
\begin{examples}
  \begin{mintednsp}{nsp}
    A=diag([3,-3,7,4,-4,8]);
    B=[eye(3,3);zeros(3,3)];
    C=[0,0,1,2,3,4;0,0,0,0,0,1];
    D=[1,2,3;0,0,0];
    w=ss2ss(syslin('c',A,B,C,D),rand(6,6));
    [A,B,C,D]=abcd(w);
    B=[B,matrix(1:18,6,3)];D=[D,matrix(-(1:6),2,3)];
    reject=1:3;
    Sys=syslin('c',A,B,C,D);
    N1=[-2,-3];C1=-N1*C;D1=-N1*D;
    nw=length(reject);nu=size(Sys.B,2)-nw;
    ny=size(Sys.C,1);nz=size(C1,1);
    [UIobs,J,N]=ui_observer(Sys,reject,C1,D1);
    W=[zeros(nu,nw),eye(nu,nu);Sys];UIobsW=UIobs*W;   
    //(w,u) --$>$ z=UIobs*[0,I;Sys](w,u)
    clean(ss2tf(UIobsW));
    wu_to_z=syslin('c',A,B,C1,D1);clean(ss2tf(wu_to_z));
    clean(ss2tf(wu_to_z)-ss2tf(UIobsW),1.d-7)
    /////2nd example//////
    nx=2;ny=3;nwu=2;Sys=ssrand(ny,nwu,nx);
    C1=rand(1,nx);D1=[0,1];
    UIobs=ui_observer(Sys,1,C1,D1);
  \end{mintednsp}
\end{examples}
%-- see also
\begin{manseealso}
  \manlink{cainv}{cainv} \manlink{ddp}{ddp} \manlink{abinv}{abinv}  
\end{manseealso}
%-- Author
\begin{authors}
  F.D.  
\end{authors}
