% -*- mode: latex -*-
\mansection{dist\_stat}
\begin{mandesc}
  \short{dist_stat}{compute mean and standard deviation of some probability distributions}
\end{mandesc}
%-- Calling sequence section
\begin{calling_sequence}
\begin{verbatim}
[m,sd]=dist_stat(dist_type [,p1,...,pk])  
\end{verbatim}
\end{calling_sequence}
  %-- Parameters
\begin{parameters}
  \begin{varlist}
   \vname{dist\_type}: a string giving the probability distribution (\verb!"bin"! for binomial, \verb!"nor"!
   for normal, \verb!"poi"! for Poisson, etc ...)
   \vname{p1, ..., pk}: (scalar) parameters (reals or integers) required to define the distribution \verb!dist_type!
    \vname{m,sd}: respectively the mean and standard deviation of the selected distribution
  \end{varlist}
  \end{parameters}
  
\begin{mandescription}

For a given distribution \verb+dist_type+ and its associated parameter(s) \verb+p1, ..., pk+ this
function computes its mean and its standard deviation.

\paragraph{Supported distributions}
\begin{itemize}

\item \itemdesc{beta}  
\verb![m,sd]=dist_stat("bet",a,b)! mean and std the \hyperlink{betapdf}{beta distribution} with 
shape parameters $a > 0$ and $b > 0$.
 
\item \itemdesc{binomial}
\item \verb![m,sd]=dist_stat("bin",n,p)! mean and std
  of the  \hyperlink{binpdf}{binomial distribution} with parameters $p \in [0,1]$ and $n$
  (positive integer). 

\item \itemdesc{negative binomial} \verb![m,sd]=dist_stat("nbn",r,p)! mean and std 
of the \hyperlink{nbnpdf}{negative binomial distribution} with parameters $r > 0$ ($r$ not
  necessarily integer) and $p \in (0,1]$. 


\item \itemdesc{Cauchy} \verb![m,sd]=dist_stat("cau",sigma)! mean and std of the  
\hyperlink{caupdf}{Cauchy distribution} parameter $\sigma > 0$.

\item \itemdesc{chi square} \verb![m,sd]=dist_stat("chi",nu)! mean and std of the 
\hyperlink{chipdf}{chisquare distribution} with parameter $\nu > 0$ (number of dof).

\item \itemdesc{non central chi square} \verb![m,sd]=dist_stat("nch",nu,lambda)! mean 
nd std of the non central chi square  distribution 
%\hyperlink{chipdf}{chisquare distribution} 
with parameter $\nu > 0$ (number of dof) and  $\lambda > 0$ (non centrality parameter).

\item \itemdesc{exponential} \verb![m,sd]=dist_stat("exp",tau)! mean and std of the  
\hyperlink{exppdf}{exponential distribution} with parameter $\tau > 0$.
Caution: the parameter is more frequently $\lambda = 1/\tau$.

\item \itemdesc{F variance ratio} \verb![m,sd]=dist_stat("f",nu1,nu2)! mean and std 
of the variance ratio distribution with parameters $\nu_1 > 0$ and $\nu_2 > 0$ 
(respectively number of dof in the numerator and denominator). 

\item \itemdesc{non central F variance ratio} \verb![m,sd]=dist_stat("nf",nu1,nu2,lambda)! 
mean and std of the non central F variance ratio distribution with parameters $\nu_1 > 0$, $\nu_2 > 0$ 
(respectively number of dof in the numerator and denominator) and $lambda \ge 0$ (non  centrality parameter).


\item \itemdesc{gamma} \verb![m,sd]=dist_stat("gam",a,b)! mean and std  of the 
\hyperlink{gampdf}{gamma distribution} with parameters $a > 0$ (shape parameter) and $b \ge 0$
  (rate parameter). Caution: second parameter is often a scale parameter, says $s = 1/b$.


\item \itemdesc{Gauss Laplace} \verb![m,sd]=dist_stat("nor",mu,sigma)! mean and std 
of the  \hyperlink{norpdf}{normal distribution} with parameters $\mu$ and $\sigma > 0$.


\item \itemdesc{geometric} \verb![m,sd]=dist_stat("geom",p)! mean and std 
of the \hyperlink{geompdf}{geometric distribution} with parameter $p \in (0,1]$.


\item \itemdesc{Laplace} \verb![m,sd]=dist_stat("lap",a)! mean and std 
of the \hyperlink{lappdf}{Laplace distribution} with parameter $a > 0$.

\item \itemdesc{logistic} \verb![m,sd]=dist_stat("logi",a,b)! mean and std 
of the \hyperlink{logipdf}{logistic distribution} with parameter $a$ and $b > 0$.

\item \itemdesc{log normal} \verb![m,sd]=dist_stat("logn",mu,sigma)! mean and std 
of the  \hyperlink{lognpdf}{log normal distribution} with parameters $\mu$ and $\sigma > 0$.

\item \itemdesc{Pareto} \verb![m,sd]=dist_stat("par",a,b)! mean and std 
of the \hyperlink{parpdf}{Pareto  distribution} with shape parameter $a > 0$ and scale parameter $b > 0$.

\item \itemdesc{Poisson} \verb![m,sd]=dist_stat("poi",mu)! mean and std 
of the \hyperlink{poipdf}{Poisson distribution} with parameter $\mu \ge 0$.


\item \itemdesc{Rayleigh} \verb![m,sd]=dist_stat("ray",sigma)! mean and std 
of the \hyperlink{raypdf}{Rayleigh distribution} with parameter $\sigma > 0$.

\item \itemdesc{tail Rayleigh} \verb![m,sd]=dist_stat("tray",sigma, a)! mean and std 
of the \hyperlink{traypdf}{tail (from $a$) of the Rayleigh distribution} with parameters $\sigma > 0$ 
and $a \ge 0$.

\item \itemdesc{Student's t} \verb![m,sd]=dist_stat("t",nu)! mean and std of 
the \hyperlink{tpdf}{t distribution} with parameter $\nu > 0$ (number of dof).


\item \itemdesc{non central Student's t} \verb![m,sd]=dist_stat("nt",nu,delta)! 
mean and std of the non central t distribution with parameters $\nu > 0$ (number of dof) and
$\delta$ (non centrality parameter).


\item \itemdesc{uniform (uin)} \verb![m,sd]=dist_stat("uin",n1,n2)! mean and std 
of the \hyperlink{uinpdf}{uniform distribution on integers $n_1,n_1+1,\dots,n_2$}.

\item \itemdesc{uniform (unf)} \verb![m,sd]=dist_stat("unf",a,b)! mean and std  
of the \hyperlink{unfpdf}{uniform distribution on the interval $[a,b]$} ($a < b$).

\item \itemdesc{Weibull} \verb![m,sd]=dist_stat("wei",a,b)! mean and std of 
the \hyperlink{weipdf}{Weibull  distribution} with scale parameter $a > 0$ and shape parameter $b > 0$.

\end{itemize}

\end{mandescription}


\begin{manseealso}
  \manlink{pdf}{pdf}, \manlink{cdf}{cdf}, \manlink{icdf}{icdf}, \manlink{grand}{grand}
\end{manseealso}

%-- Authors

\begin{authors}
  Buno Pincon
\end{authors}

