% -*- mode: latex -*-
%% Scilab ( http://www.scilab.org/ ) - This file is part of Scilab
%% Copyright (C) 1987-2016 - (INRIA)
%%
%% This program is free software; you can redistribute it and/or modify
%% it under the terms of the GNU General Public License as published by
%% the Free Software Foundation; either version 2 of the License, or
%% (at your option) any later version.
%%
%% This program is distributed in the hope that it will be useful,
%% but WITHOUT ANY WARRANTY; without even the implied warranty of
%% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
%% GNU General Public License for more details.
%%
%% You should have received a copy of the GNU General Public License
%% along with this program; if not, write to the Free Software
%% Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307  USA
%%                                                                                

\mansection{iir}
\begin{mandesc}
  \short{iir}{iir digital filter} \\ % 
\end{mandesc}
%\index{iir}\label{iir}
%-- Calling sequence section
\begin{calling_sequence}
\begin{verbatim}
  [hz]=iir(n,ftype,fdesign,frq,delta)  
\end{verbatim}
\end{calling_sequence}
%-- Parameters
\begin{parameters}
  \begin{varlist}
    \vname{n}: filter order (pos. integer)

    \vname{ftype}: string specifying the filter type \verb!'lp','hp','bp','sb'!

    \vname{fdesign}: string specifying the analog filter design
    \verb!='butt','cheb1','cheb2','ellip'!

    \vname{frq}: 2-vector of discrete cut-off frequencies (i.e.,
    \verb!0$<$frq$<$.5!). For \verb!lp! and \verb!hp! filters only \verb!frq(1)!
    is used. For \verb!bp! and \verb!sb! filters \verb!frq(1)! is the lower
    cut-off frequency and \verb!frq(2)! is the upper cut-off frequency

    \vname{delta}: 2-vector of error values for \verb!cheb1, cheb2!, and
    \verb!ellip! filters where only \verb!delta(1)! is used for \verb!cheb1!
    case, only \verb!delta(2)! is used for \verb!cheb2! case, and
    \verb!delta(1)! and \verb!delta(2)! are both used for \verb!ellip!
    case. \verb!0$<$delta(1),delta(2)$<$1!
    \begin{itemize}
    \item for \verb!cheb1! filters \verb!1-delta(1)$<$ripple$<$1! in passband
    \item for \verb!cheb2! filters \verb!0$<$ripple$<$delta(2)! in stopband
    \item for \verb!ellip! filters \verb!1-delta(1)$<$ripple$<$1! in passband
      and \verb!0$<$ripple$<$delta(2)! in stopband \end{itemize}
  \end{varlist}
\end{parameters}
\begin{mandescription}
  function which designs an iir digital filter using analog filter designs.
\end{mandescription}
%--example 
\begin{examples}
  \begin{mintednsp}{nsp}
    hz=iir(3,'bp','ellip',[.15 .25],[.08 .03]);
    [hzm,fr]=frmag(hz,256);
    xbasc();plot2d(fr',hzm',style=2)
    xtitle('Discrete IIR filter band pass  0.15 < fr < 0.25 ',' ',' ');
    q=poly(0,'q');     //to express the result in terms of the ...
    hzd=horner(hz,1/q,ttmode=%t) //delay operator q=z^-1
  \end{mintednsp}
\end{examples}
%-- see also
\begin{manseealso}
  \manlink{eqfir}{eqfir} \manlink{eqiir}{eqiir}  
\end{manseealso}
%-- Author
\begin{authors}
    Carey Bunks  
\end{authors}
