% -*- mode: latex -*-
%% Scilab ( http://www.scilab.org/ ) - This file is part of Scilab
%% Copyright (C) 1987-2016 - (INRIA)
%%
%% This program is free software; you can redistribute it and/or modify
%% it under the terms of the GNU General Public License as published by
%% the Free Software Foundation; either version 2 of the License, or
%% (at your option) any later version.
%%
%% This program is distributed in the hope that it will be useful,
%% but WITHOUT ANY WARRANTY; without even the implied warranty of
%% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
%% GNU General Public License for more details.
%%
%% You should have received a copy of the GNU General Public License
%% along with this program; if not, write to the Free Software
%% Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307  USA
%%                                                                                

\mansection{rpem}
\begin{mandesc}
  \short{rpem}{RPEM estimation} \\ % 
\end{mandesc}
%\index{rpem}\label{rpem}
%-- Calling sequence section
\begin{calling_sequence}
\begin{verbatim}
  [w1,[v]]=rpem(w0,u0,y0,[lambda,[k,[c]]])  
\end{verbatim}
\end{calling_sequence}
%-- Parameters
\begin{parameters}
  \begin{varlist}
    \vname{a,b,c}: \verb!a=[a(1),...,a(n)], b=[b(1),...,b(n)], c=[c(1),...,c(n)]!
    \vname{w0}: \verb!list(theta,p,phi,psi,l)! where:
    \begin{varlist}
      \vname{theta}: [a,b,c] is a real vector of order \verb!3*n!
      \vname{p}: (3*n x 3*n) real matrix.
      \vname{phi,psi,l}: real vector of dimension \verb!3*n!
    \end{varlist}
    During the first call on can take:
\begin{verbatim}
  theta=phi=psi=l=0*ones(1,3*n). p=eye(3*n,3*n)
\end{verbatim}
    \vname{u0}: real vector of inputs (arbitrary size) (if no input take \verb!u0=[ ]!).
    \vname{y0}: vector of outputs (same dimension as \verb!u0! if \verb!u0! is not empty). (\verb!y0(1)! is not used by rpem).
    If the time domain is \verb!(t0,t0+k-1)! the \verb!u0! vector contains the inputs 
    \verb!u(t0),u(t0+1),..,u(t0+k-1)! and \verb!y0! the outputs 
    \verb!y(t0),y(t0+1),..,y(t0+k-1)!
  \end{varlist}
\end{parameters}
\begin{mandescription}
  Recursive estimation of parameters in an ARMAX model.
  Uses Ljung-Soderstrom recursive prediction error method.
  Model considered is the following:
\begin{verbatim}
  y(t)+a(1)*y(t-1)+...+a(n)*y(t-n)=
  b(1)*u(t-1)+...+b(n)*u(t-n)+e(t)+c(1)*e(t-1)+...+c(n)*e(t-n)
\end{verbatim}
The effect of this command is to update the estimation of
unknown parameter \verb!theta=[a,b,c]! with
\verb!a=[a(1),...,a(n)], b=[b(1),...,b(n)], c=[c(1),...,c(n)]!.
\end{mandescription}
%-- section-Optional parameters
\paragraph{Optional parameters}
\begin{itemize}
\item \itemdesc{lambda}: optional parameter (forgetting constant) choosed close to 1 as convergence occur:\verb!lambda=[lambda0,alfa,beta]! evolves according to:
\begin{verbatim}
  lambda(t)=alfa*lambda(t-1)+beta 
\end{verbatim}
with \verb!lambda(0)=lambda0!\verb!k!: contraction factor to be chosen close to 1 as convergence occurs.\verb!k=[k0,mu,nu]! evolves according to:
\begin{verbatim}
  k(t)=mu*k(t-1)+nu 
\end{verbatim}
with \verb!k(0)=k0!.\verb!c!: large parameter.(\verb!c=1000! is the default value). 
\end{itemize}
%-- section-Output parameters:
\paragraph{Output parameters:}
\verb!w1!: update for \verb!w0!.\verb!v!: sum of squared prediction errors on \verb!u0, y0!.(optional).
In particular \verb!w1(1)! is the new estimate of \verb!theta!. If a new sample \verb!u1, y1! is available the update is obtained by:\verb![w2,[v]]=rpem(w1,u1,y1,[lambda,[k,[c]]])!. Arbitrary large series can thus be treated.

