% -*- mode: latex -*-
\mansection{fstabst}
\begin{mandesc}
  \short{fstabst}{Youla's parametrization} \\ % 
\end{mandesc}
%\index{fstabst}\label{fstabst}
%-- Calling sequence section
\begin{calling_sequence}
\begin{verbatim}
  [J]=fstabst(P,r)  
\end{verbatim}
\end{calling_sequence}
%-- Parameters
\begin{parameters}
  \begin{varlist}
    \vname{P}: \verb!syslin! list (linear system)
    \vname{r}: 1x2 row vector, dimension of \verb!P22!
    \vname{J}: \verb!syslin! list (linear system in state-space representation)
  \end{varlist}
\end{parameters}
\begin{mandescription}
  Parameterization of all stabilizing feedbacks.\verb!P! is partitioned as follows:
\begin{verbatim}
  P=[ P11 P12;
      P21 P22]  
\end{verbatim}
(in state-space or transfer form: automatic conversion in state-space is
done for the computations)\verb!r! = size of  \verb!P22! subsystem, (2,2) block of \verb!P!
\begin{verbatim}
  J =[ J11 J12;
       J21 J22]
\end{verbatim}
\verb!K! is a stabilizing controller for \verb!P! (i.e. \verb!P22!) iff 
\verb!K=lft(J,r,Q)! with \verb!Q! stable.
The central part of \verb!J! , \verb!J11! is the lqg regulator for \verb!P!
This \verb!J! is such that defining \verb!T! as the 2-port \verb!lft! of \verb!P!
and \verb!J!: \verb![T,rt]=lft(P,r,J,r)! one has that \verb!T12! is inner
and \verb!T21! is co-inner.
\end{mandescription}
%--example 
\begin{examples}
  \begin{mintednsp}{nsp}
    ny=2;nu=3;nx=4;
    P22=ssrand(ny,nu,nx);
    bigQ=rand(nx+nu,nx+nu);bigQ=bigQ*bigQ';
    bigR=rand(nx+ny,nx+ny);bigR=bigR*bigR';
    [P,r]=lqg2stan(P22,bigQ,bigR);
    J=fstabst(P,r);
    Q=ssrand(nu,ny,1);Q.A=-1;  //Stable Q
    K=lft(J,r,Q);
    A=h_cl(P,r,K); spec(A)
  \end{mintednsp}
\end{examples}
%-- see also
\begin{manseealso}
  \manlink{obscont}{obscont} \manlink{lft}{lft} \manlink{lqg}{lqg} \manlink{lqg2stan}{lqg2stan}  
\end{manseealso}
